\documentclass[a4paper,12pt]{article}
\usepackage[utf8]
{inputenc}

\begin{document}

\title{Mission 7: Information - v3}
\author{LinkPactGames}
\date{October 2014}
\maketitle

\section{Summary}

\textit{The player goes off to a corrdinate provided by Ente. On the way the player dispatches a following rebel group.
At the information point the player get some information about the sector, and information about where to go next
in order to find the radar-distruptor technology.}

\section{Story points}

\textgreater To coordinate, Sair: Comment\\
\textgreater x To coordinate, following rebels: Conflict\\
o At coordinate, Sair - Evaluating information

\section{Manus}

\subsection{Travelling to coordinate}

[Sair] "It looks like we are followed. We can't lead them to the information hub." 

[Sair] "Either we'll have to shake them off, or we will have to make sure they can't follow us anymore."

...

[Sair] "They won't stop following us. We will need to do something about them."

...

[Rebel] "What are you doing? I will report this to the command!"

... Dispatching followers ...

[Sair] "That was all of them.."

... Closing in to the information hub ...

[Sair] "This must be it. Well hidden, indeed!"

\subsection{At information hub}

[Sair] "So, let's see what we have here. I'll enter the password we got from Ente.."

[Sair] "..."

[Sair] "We have access."

[Sair] "..."

[Sair] "..."

[Sair] "Interesting. It's a lot of information here about both the Alliance and the rebels."

[Sair] "It seems like the official story about how the Alliance came to power might be slightly.. altered."

[Sair] "Yes, they came to power through an election. But the elections doesn't seem to have been as free as they claim..."

[Sair] "The rebels on the other hand seems to have started as an anarchist organization, attempting to 'liberate' the sector
through spreading chaos and disorder."

[Sair] "They seem to have gradually adapted over time to be more... presentable... for the people around here."

[Sair] "But that's not why we are here. I wish we had found this place earlier..." (Hint about a side-mission?)

[Sair] "I think I have found their information about Murt."

[Sair] "It seems like after they increased the range of their scanners, they started to pick up huge signals from a particular asteroid outside New Norrland."

[Sair] "That must be it. I have recorded the coordinates. Now we only need to find data on that cloak-technology.."

[Sair] "..."

[Sair] "Here it is. Quite recently they started to develop a cloaking technology on another outpost close to Peye."

[Sair] "We should go there immediately. I have downloaded the data. I will process it on the way."

[Sair] "I have marked the coordinate on the map. I will tell you more during travel."

\end{document}




























