\documentclass[a4paper,12pt]{article}
\usepackage[utf8]
{inputenc}

\begin{document}

\title{Mission 7: Information - v1}
\author{LinkPactGames}
\date{October 2014}
\maketitle

\section{Summary}

\textit{The player goes off to a corrdinate provided by Ente. On the way the player dispatches a following rebel group.
At the information point the player get some information about the sector, and information about where to go next
in order to find the radar-distruptor technology.}

\section{Story points}

\textgreater To coordinate, Sair - Comment\\
\textgreater x To coordinate, following rebels - Conflict\\
o At coordinate, Sair - Evaluating information

\section{Manus}

\subsection{Travelling to coordinate}

[Sair] "What do you think will happen with Ente? Rok looked quite sinister. It will not be a nice day for him."

[Sair] "It looks like we are followed. We can't lead them to the information hub. Either we'll have to shake them of, or we
will have to make sure they can't follow us anymore."

[Sair] "They won't stop following us. We will need to do something about them."

[Rebel] "What are you doing? I will report this to the command!"

... Dispatching followers ...

[Sair] "That was all of them.."

... Closing in to the information hub ...

[Sair] "This must be it. Well hidden, indeed!"

\subsection{At information hub}

[Sair] "So, let's see what we have here. I'll enter the password we got from Ente.."

[Sair] "..."

[Sair] "We have access. Let's see what we have here."

[Sair] "..."

[Sair] "..."

[Sair] "Interesting. They are writing about how the Alliance came into power. Before them there seems to have been a weak
coalition between the different planets, where some planets had single persons in power, and other all people got to vote."

[Sair] "The situation started to worsen when the resources started going out. People started to grow more and more worried.
Groups of pirates started appearing in the sector, which couldn't be controlled by the coalitions collected forces."

[Sair] "One day the pirates banded together. They started calling themselves 'rebels', and said that they would 'liberate' the sector
from the coalition. Many people joined them, especially from New Norrland and Lavis who was hit in particular by the resouce decline."

[Sair] "The coalition had nothing against the rebels growing force. Until another factor came into play. Fortrun was already then the richest planet
in the sector, and was lead by a small group of leaders. They started putting all their resources into military research, and started lobbying for themselves
in the coaltion."

[Sair] "Soon the planets started gathering around and supporting Fortruns growing military. It was their only hope to fend of the rebels. Fortruns strength grew
rapidly, and they started taking more and more control in the coalition until they one day were able to push out the rebels from the sector."

[Sair] "At this time, they had an incredible strength though, and they put themselves in the role of the guardian of the sector. They started meddling in all the planets
business, using their resources with the explanation that it was needed for the protection of the sector."

[Sair] "They also started to update the history of the sector. They were afraid that people would want to go back to sharing power between the planets, so they tried
and succeeded in removing the Coalition from the collective databank."

[Sair] "..."

[Sair] "That was the end of that article. This document is dated several decennia ago though. Maybe both the Alliance and the rebels have changes since then? 
Let's focus on what we are here for. The conceling-mechanism and the coordinates for the meteor."

[Sair] "I've got the coordinates. Let's leave. I have downloaded the data. I can continue to work with it on the way."

[Sair] "For now, let's go to the coordinate X. I have marked it on the map. I will tell you more on the way."

\end{document}




























