\documentclass[a4paper,12pt]{article}
\usepackage[utf8]
{inputenc}

\begin{document}

\title{Mission 3: Defend Colony - v1}
\author{LinkPactGames}
\date{October 2014}
\maketitle

\section{Summary}

The rebels have occupied an area on New Norrland. This affects both people in
the vicinity, and the Alliance itself as it interferes with Alliance
mining interests. The player joins an Alliance fleet which successfully
repels the rebels.

\section{Story points}

o At Fortrun, Ai and Par - Discussion about rebels. Told to participate.\\
o Outside Fortrun, Ai - The fleet takes of\\
\textless Travelling to New Norrland - Talking with Ai and others
o Outside New Norrland, Ai - Talks to the fleet
x Mission - Taking control over the mine
o At New Norrland, other pilots - Reflection over the situation
x Mission - Defending the mine
o At New Norrland - Celebrations and civil input
\textless Travelling to Fortrun, speaking with Sair
o At Fortrun, Ai and commander - Well done, come back later

\section{Manus}

\subsection{At Fortrun}

"Come in, join us." Ai waves you to follow her into a crowded room.
The center of attention is an old man with a hard stare. You identify him
as the Alliance's commander.

The commander turns to the group. "Some of you who are knows why we have gathered,
while others don't. Most of you are aware of our crucial mining operations on New
Norrland. This is the larges rebel offensive up to date. They have managed to control
of the entire mine, and large parts of the surrounding land. This is an emergency for
both us and the locals on the planet."

The commander stares fiercely at the crowd. "We have gathered all available pilots. 
We must strike hard and decisively. We must show the rebels that they can't have their 
ways in this sector. That we cannot tolerate their chaos and violence."

"The fleet leaders have been provided with instructions. They will further them to
their respective fleets".

The commander leaves the room. A worried mumble spreads in the crowd.

"...they have never been so coordinated..."

"...what are they thinking? ...what are the locals thinking?..."

Ai turns to you and the rest of her squad. She stares fiercely at all of you.

"This needs to be done. If we don't act now, it sends a signal to the rebels that
we aren't capable of handling them. Let's strike them down, show them that they
cannot be allowed to interfere with the people of this sector."

"We will meet outside in a moment. I will give you further instructions when it is time."
Ai left the room.

Ai's short speech seems to have improved the mood of her squad. They seem to trust her
judgement. Some of them nods approvingly to each other, before silently leaving for their ships.

\subsection{Outside Fortrun}

[Sair] "Something is different with this mission. On the previous missions, the other pilots
seems to have been quite confident about what they were getting themselves into. This seems
to be new and unknown for most of them. Maybe this shows that the rebels are growing out
of their control. Stay safe."

[Ai] "Everyone is here? Good. Let's go."

\subsection{Travelling to New Norrland}

[Other squad member] ..I don't know about this.. One more salary, and I would have had that
Durable Shield. I would have felt much safer with that equipped compared to this Basic Shield.

[Other squad member] ..Even if they are getting more and more numerous, they still have much
weaker ships than us. They don't seem afraid of collateral damage though. Keep away from those
terrible mines and bombs.

[Other squad member] ..Yeah.. I heard that they have focused on building more explosives.
I have heard rumours about ships spitting bombs exploding at huge area at you. I think
it is possible to explode the bombs through firing at them though..

[Other squad member] ..I wonder how they treat the civilians around the mines. There is a
quite large city nearby which they must have occupied. I hope they are ok..

\subsection{At New Norrland}

Ai halts the squad. "It is time. Our task in this operation is to secure one of the mines
as quickly as possible, to prevent the rebels from destroying it. Then, we must hold or positions
until the other squads has secured the area."

"Intel tells us they have an increased presence of explosive ships in the area. That means
that we will encounter bomb ships and mine layers. Keep mobile, and make sure you don't become
trapped by their mine fields. If you do, try to fire your way through."

"It is time. In this first attack focus is to get through them. Don't worry about shooting
down more than needed to clear the path. Let's go."

...Level...

[Ai] "Well done, we are through. Now we need to keep our position here for long enough.
Another squad is on the way. Keep your focus."

...Level...

[Ai] "The area is under our control. Increadible work everyone."
She sounds relieved.

\subsection{Travelling to Fortrun}

[Civilian] "...Is this thing working? I want to tell you, ship 90, that not everyone here
approves of your presence. You don't care about the civilians, don't you? All you care
about is your mine, your profit, and to make sure you can live your cozy lives at Fortrun.
People are starving here. The rebels aren't good either, but at least they aren't sucking
out our resources under the pre..." The connection is abruptly ended.

[Sair] "It seems that his transmission only managed to target us. Of course there has to
be some people not so happy about the Alliance here. There always are. But do they really
think that the rebel anarchy is to prefer? You should ask Ai what she thinks when we have
returned to Fortrun."

\subsection{At Fortrun}

Ai's face hardens as she hears what you heard. Then she calmly answers. "People don't
realize what we actually do for them. I really doubt that anyone would prefer the rebel
anarchy in reality, when they realize that they can't manage the small resources we have.
We are doing what we must in order to limit chaos and starvation. But that is of course
not enough for everyone. They don't like being controlled, and I understand that.
But like a child, you cannot always do exactly as you would like. Noone can. Not them, not us."

She stares into the air another moment, before turning to you again.

"Nevertheless. You did a fantastic job back there. We suffered very low casualities compared
to the rest of the squads, and overall it ended much better than it could have. You should
get some rest. Come back here then. We will have more missions for you."

You and Ai leaves the room. You go back to your ship.

[Sair] "There seems to be a lot going on under the surface here. It could be interesting
asking around a bit on Fortrun and other planets, to hear what people are thinking. Anyway,
let's get some rest, and then return to Ai."

\end{document}













