\documentclass[a4paper,12pt]{article}
\usepackage[utf8]
{inputenc}

\begin{document}

\title{Mission 4: Infiltration - v2}
\author{LinkPactGames}
\date{October 2014}
\maketitle

\section{Summary}

\textit{The player is sent to infiltrate the rebels. The player provide
the rebels with information about an imminent attack. The allied
fleet is caught in an ambush, and there the player joins the rebels.}

\section{Story points}

o Fortrun, Ai: Told about mission and reasoning about it\\
o Outside Fortrun, Sair: Brief discussion on the subject\\
\textgreater Travel, Sair: Brief comment\\
o Location outside solar system, Rebel Rok: Information leak\\
\textgreater Travel, Sair: brief\\
o Attack location, fleet: Sceptical discussion, attack, talk with rebels\\
\textgreater Travel, Rok: Aftertalk

\section{Manus}

\subsection{At Fortrun}

Ai turns to you with a serious look on her face.

[Ai] "I just returned from a meeting with the command."

[Ai] "We have a great favour to ask from you. But first I should tell you a bit more
about the situation."

[Ai] "You have heard about our research on the mineral Murt." 

[Ai] "We have made progress lately. We have very small quantities of the mineral though."

[Ai] "I we would manage to find greater amounts of the mineral, it could become an important
factor in raising this sector back on its feet."

[Ai] "On the other hand, it could also be used for creating almost unimaginable weapons, shields
and bombs."

[Ai] "We have reasons to believe that there somewhere in the sector exists a great source of Murt." 

[Ai] "We think the the rebels knows about this." 

[Ai] "If they gained access to it, it would be a huge catastrophy." 

[Ai] "We must stop them from gaining access to this mineral at any cost."

[Ai] "It is here you comes in. We need an insider. Someone they can trust, who can
provide us with insight in what they know and what they plan."

[Ai] "You are a skilled and trusted pilot and you are unknown for them." 

[Ai] You could be one of the rats, leaving Alliance for the gold and green forests that the rebels promise."

[Ai] "Our plan is to let you leak crucial information to them about a coming attack against
one of their outposts near Lavis." 

[Ai] "You will join them during the attack. You will be sent their together with a group of suspected
rats." 

[Ai] "You and the rebels will help us get rid of them, and at the same time
lay a foundation of trust for you."

[Ai] "I have set up a meeting with a lower rebel leader at coordinates (X,X)." 

[Ai] "You should travel there immediately, and hand him this file. 

[Ai] "Then, you will travel to the outpost and join the attack fleet. I will provide you with the exact coordinates
after the meeting."

She looks at you seriously. "Good luck. I will stay in touch. Go now."

\subsection{Outside Fortrun}

[Sair] "That was unexpected. But it might be the logical choice. Let's go meet that rebel person."

\subsection{Travelling to meeting location}

[Sair] "You know. This might be the last moment of stillness we get in a while."

[Sair] "You should take a moment to appreciate it."

\subsection{Meeting Rok}

A young man with a fierce look appears on your display.

[Rok] "So you came after all. And you seems to have no company. Brave!"

[Rok] "Stupid, and brave.. Let's get to it. You had information. Sent it over."

He speaks with a quite harsh voice. It sounds like he isn't as confident with
the situation as he tries to appear. 

You transfer the information.

[Rok] "..."

[Rok] "... Why would you tell us this. A change of heart you say?" 

[Rok] "I have difficulties believing you. But I also have difficulties understanding you."

[Rok] "..."

[Rok] "I will leave you now. If this is true, and you follow the plan through,
there will be a place for you by us." 

[Ai] "If not... I will make sure you regret this meeting."

[Rok] "Bye for now."

The screen goes blank, and the small group leaves silently.

[Sair] "That was tense. It wouldn't have been illogical for them to shoot us down at the spot."

[Ai] "..Did it go as planned? Good. Now, join the attack fleet at coordinate (X, X)." 

[Ai] "There is no looking back now. This might be our best chance to get a grip on the rebels."

\subsection{Travelling to attack location}

[Sair] "Remember. Even if the Alliance fleet we will join is mainly quite
unexperienced pilots, they will have better equipment than most of the rebels
we have faced this far."

[Sair] "Be careful."

\subsection{Meeting attack fleet}

A rough and seemingly annoyed man appears on your display.

[Attack fleet leader] "You are late, scum. This is not a walk in the park."

[Attack fleet leader] "I will not watch your back if you not are able to follow orders."

He directs his next message to the entire fleet.

[AFL] "I will not hold a fucking inspirational speech for you. Do your job,
and we can go home." 

[AFL] "I don't know what they are fucking thinking, sending us here. I guess someone has to do their dirty job."

[AFL] "We will try to make this as quick as possible. Go in, destroy everything,
and leave.

[AFL] "Make sure they don't have time to forward the message, or we will be swarmed on our way back."

[AFL] "Let's move out. Don't fall behind."

\subsection{Attack on Alliance}

... Mostly empty level ...

[AFL] "What is this? Is the station abandoned?"

Rebels appear on your radar.

[AFL] "What? We are surrounded!" 

[AFL] "Someone has ratted us out. Pull out. Pull the fuck out!"

[Rok] "You came here after all. Well done. Now, let's finish this."

[Sair] "I'm not looking forward to this. Let's get this over with."

... Attack on Alliance with the rebels ...

[AFL] "Are you fucking kidding me? What are you doing, idiot?"

[AFL] "What did they promise you? Gold and happiness?" 

[AFL] "Oh, your dreams will turn to ashes. You will regret this. You will really reg.."

A rebel bomb interrupts the attack fleet leaders inspirational speech.

[Rok] "Don't let them escape. Let's pay back for all that they have done to us."

... The connection was aborted. The level begins, and ends ...

Rok appears, looking relieved and excited.

[Rok] "Amazing job my friend! We really got them there." 

[Rok] "They will think one time or two before attacking us again."

[Rok] "We would not have been able to do it without you. We really appreciate it."

[Rok] "A small, but significant step towards the peoples liberation. Thank you."

[Rok] "Travel to the coordinates (X,X). There you will find our base." 

[Rok] "I will tell you more about us, and you will tell us more about you." 

[Rok] "You will get a place with us rebels. You will not regret this choice. See you later!"

\subsection{Travel with rebels to base}

[Ai] "It went as expected? Good. 

[Ai] "I feel slightly bad for putting you through this, but it was a necessity." 

[Ai] "I'm sure you understand."

[Ai] "Don't get fooled by them. Many of them themselves believe that they
are standing for good and justice.

[Ai] "Remember all the people they plundered and murdered around the system."

[Ai] "I wish you best of luck. Contact me immediately when you find anything useful."

..connection ended..

\end{document}













