\documentclass[a4paper,12pt]{article}
\usepackage[utf8]
{inputenc}

\begin{document}

\title{Mission 1: Rebels in the Meteors - v4}
\author{LinkPactGames}
\date{Novembre 2014}
\maketitle

\section{Summary}
\textit{The player arrives at Border Station to do his first real mission
for the Alliance. He, and a small group of Alliance ships, scouts a nearby meteor field
for rebels. They are attacked by the rebels, and defeats them.}

\section{Story points}

o Border Station, Bert: Welcomed to Border Station, given mission specifications\\
o Outside Border Station, fleet leader: Welcomed to the fleet, taking of\\
\textgreater  Travelling to meteor belt, Sair: Casually talking with the Talking Ship\\
o Meteor belt, Alliance: Talking about the pirates\\
x Scout/shooting pirates: Level (with tutorial text)\\
o Meteor belt, captain: Level well done!\\
\textgreater  Travelling back, Sair: Brief comment\\
o At Border Station, Bert: Well done! Recommend to friend! Go to Highfence!

\section{Manus}

\subsection{At Border Station}

"You must be the new pilot, right?" A middle-aged man eyes you carefully.
"I am Berr, and I am coordinating the pilots here at Border Station."

"Previously, my job was to keep track of our transport ships. Lately, the
rebels have become an increasing problem. Both here and in the rest of the sector."

"Currently, a small rebel fleet is hiding in a nearby asteroid belt"

"They are not a threat against the Border Station itself, but they raid and plunder ships
and transports that travel between the Border Station and the planet Lavis."

"We must stop them now, before they do any more damage." 

"A small fleet will soon leave to search the asteroid belt for rebels. You should join them.
You might learn a thing or two."

\subsection{Outside Border Station}

[Captain] "Another rookie? Fantastic! Stay close to us veterans, and
you might even be helpful!" 

[Captain] "We are leaving now. Over and out."

\subsection{Travelling to Meteor Belt}

[Sair] "So this seems to be going quite well. I hope you are focused."

[Sair] "I would really dislike getting holes blasted in the hull."

[Captain] "So rookie. I see you have one of those silly talking ships?" 

[Captain] "Bahaha! Don't let it distract you."

[Sair] "..."

\subsection{At Asteroid Belt}

[Captain] "Let's see.." 

[Captain] "According to our scans, this rebel group should have much weaker weapons than us."

[Captain] "This will probably be an easy mission, but let's stay cautious."

[Captain] "They often make up for their poor firepower by sheer numbers."

[Captain] "We want to shoot down as many of them as possible, but rather let a rebel ship slip through than take a hit."

[Captain] "The goal is to scare them off, not to eradicate them."

... Level begins ...

[Captain] "Stay clear of those asteroids. Don't waste your energy on them."

[Captain] "Here they come! Stay close, shoot down as many as you can." 

[Captain] "Remember, you fire by pressing and holding the ACTIONKEY1." 

[Captain] "Give them hell rookie, give them hell."

...Level ends...

[Captain] "That's a job well done!" 

[Captain] "That should keep them away for a while. Well done, rookie. Your [number of shot down ships] downed ships really made a difference."

[Captain] "I will make sure you are rewarded accordingly. Now, let's head back to Border Station."

\subsection{Travelling back from Asteroid Belt}

[Sair] "That is one annoying captain..." 

[Sair] "Nevertheless, the mission went well. A successful first mission."

\subsection{At Border Station}

You are greeted by Berr. 

[Berr] "Well done, well done! Keep it up, and you will have loads of opportunities
in the Alliance." 

[Berr] "Here is your reward! XX rupees, plus a bonus XX for the ships you brought down. 

[Berr] "This weapon could also be of use for you. It is called a 'Spread Bullet', a powerful close-range weapon."

[Berr] "You are able to equip up to two primary weapons at a time. This means you could use both the Basic Laser and 
the Spread bullet in a single level."

[Berr] "You can toggle between your equipped weapons during a level using ACTIONKEY2."

Berr's expression turns more serious. He looks thoughtful.

[Berr] "The sector is troubled right now. Resources are running out one after another,
and rebel attacks get more frequent."

[Berr] "The Alliance is doing its best to keep up, but we are slowly losing control over the sector. It's hard to defend
everyone from the rebel raids"

[Berr] "A pilot like you would really be helpful."

[Berr] "You should go to Highfence. A woman called Ai currently leads their military operations."

[Berr] "She will certainly have some work for you. I will send her my recommendations."

[Berr] "That's all for now. Stay safe."

\end{document}













