\documentclass[a4paper,12pt]{article}
\usepackage[utf8]
{inputenc}

\begin{document}

\title{Mission 10: The End, Rebel branch - v1}
\author{LinkPactGames}
\date{October 2014}
\maketitle

\section{Summary}

\textit{The player helps the Alliance wringing the Murt from the rebels hands. Military factions
of the rebels are eliminated or dissolved. The war is over. The Aliance is in total control.}

\section{Story points}

o Alliance fleet, Ai - Ai explains the Alliance position\\
\textgreater Asteroid belt - The player and the Alliance move in\\
ox Murt - The Alliance wrings the control over Murt out of the rebels hands\\
\textgreater \textgreater Alliance Ending

\section{Manus}

\subsection{Alliance Fleet}

[Ai] "Long time, no see! It is good to finally see you again."

[Ai] "I will tell you what we know about what's going on. We have known since a while that the scientist has located
something which they doesn't want to tell anyone about. We believe that it is a huge quantity of Murt."

[Ai] "After you kidnapped that scientist the rebels suddenly started gathering a large fleet of ships, travelling here.
They abandoned many of their stations, even suddenly abandoning raids against transports."

[Ai] "This was the signal. They had managed to extract information about the Murt position from the scientist."

[Ai] "We moved out immediately, but we was unprepared for which speed the rebel was able to gather their forces."

[Ai] "They were here before us, and has had more time to scan the asteroids. We believe they are able to take control
over it any minute now."

[Ai] "It would be a catastrophy. We wouldn't be able to contain them anymore. They would be able to roam free,
plundering and spreading chaos throughout the sector."

[Ai] "You will be needed here, so make sure you'll stay around. This will be a tough one."

Do you want to share about Murt with Ai?\\
\textgreater Tell her what you know.\\
\textgreater Not yet, I want to check the other options.

[Ai] "What is it you are telling me? You knew all this without telling me until now? Why!"

[Ai] "We don't have time to take that discussion now. I'm glad you came to your senses anyway. We should move out
immediately. Maybe there still is time to get to the Murt before the rebels. This could tip everything in our favour."

\subsection{Asteroid Belt}

[Ai] "It must be that asteroid. It is swarmed by rebels, goddammit!"

[Ai] "They seem defensive. They don't have access to the Murt yet. When they do, we will stand no chance.
But we are still stronger than them."

[Ai] "Our only option is to throw the dice, and hit them with what we've got. Let's break down their defenses."

... Eradication level ...

[Ai] "We are almost there. Now, we must take control over Murt. Hit them hard and fast."

... Taking control over Murt-level ...

\subsection{Murt}

A battle is raging around the asteroid, but the Alliance troops holds a small circle around the Murt asteroid.

[Ai] "Yes! We have won! We have control over Murt."

[Ai] "Let's show them the Alliance's power. Let's show them what happens if you oppose us."

[Ai] "Let's show them who rules this sector!"

\subsection{Ending}

[TO BE WRITTEN]

\end{document}




























