\documentclass[a4paper,12pt]{article}
\usepackage[utf8]
{inputenc}

\begin{document}

\title{Endings - v3}
\author{LinkPactGames}
\date{October 2014}
\maketitle

\section{Rebel ending}

After that the rebels took control over Murt, they intensified their raids against the Alliance.
Soon they controlled New Norrland, Lavis and much of the interspacial territory.
The Alliance was initially paralyzed, losing battle after battle. But after a while they started
putting up harder resistance.
The rebels became the stronger faction, but as their power grew they became more and more fractured.
Soon the rebels splitted in three different factions, all with different beliefs about how to rule the system.
The war went on for a long time.\\

At the same time, the rebels and the Alliance managed to agree on keeping a no-war-zone around Peye.
There, research could focus on how to use the Murt to help the people of the sector. They managed to create technology that
could yield food for millions of people. People weren't starving anymore.\\

You and Sair continue to travel the sector. Maybe you are helping people, maybe not.
Sometimes you wonder if you made the best choice. You will never know.\\\\
But you know that you did what you could.\\\\
The End

\section{Alliance ending}

After that the Alliance got Murt under their control they slowly started stablizing the sector part by part.
The rebels initially put up fierce resistance, throwing whatever they had against the Alliance force, but it was in vain. 
People started leaving the rebels, quicker and quicker, getting back to trying to get their everyday lives around.
The remaining rebel fleets that put up resistance were easily defeated and disbanded.\\

After the defeat of the rebels the Alliance started using part of the Murt to build and organize policing forces that were
spread out over the entire sector. Their purpose was to make sure that events like this would never happen again. 
They started controlling the information flow in the sector. It was peace, but it was a forced peace.\\

At the same time, the Alliance gave parts of the Murt to the scientists on Peye who started researching how to use the Murt
to help the people of the sector. Together they managed to create
technology that could yield food for millions of people. People weren't starving anymore.\\

You and Sair continue to travel the sector. Maybe you are helping people, maybe not.
Sometimes you wonder if you made the best choice. You will never know.\\\\
But you know that you did what you could.\\\\
The End

\section{Burn ending}

[Sair] "Do you see anything? Do you feel anything?"

[Sair] "I think this is the end. I'm going out soon."

[Sair] "Do you think we made the right choice?"

[Sair] "..."

[Sair] "I guess we'll never know."

[Sair] "But we did what we could."

[Sair] "..."

[Sair] "Goodbye. It was nice travelling with you."

[Sair] "..."

\end{document}