\documentclass[a4paper,12pt]{article}
\usepackage[utf8]
{inputenc}

\begin{document}

\title{Mission 10: The End, Rebel branch - v4}
\author{LinkPactGames}
\date{Novembre 2014}
\maketitle

\section{Summary}

\textit{The player helps the rebels accessing and keeping control over Murt. The tides are turned.
The sector now has two dominant factions, and is thrown into a deeper war.}

\section{Story points}

o Rebel fleet, Rok - Rok explains rebel position\\
\textgreater Asteroid belt - The player and the rebels move in, seizing the Murt\\
ox Murt - The rebels defends Murt, extracting, and beating back the Alliance\\
\textgreater \textgreater Rebel Ending

\section{Manus}

\subsection{Rebel Fleet}

[Rok] "There you are! I'm glad you came."

[Rok] "After some persuasion, the scientist told us many interesting things."

[Rok] "He told us about an enourmous quantity of Murt, which apparently is located somewhere in this asteroid belt."

[Rok] "It is only a matter of time before we will know which asteroid that contains the Murt."

[Rok] "The Alliance has also somehow picked up the information. This makes the situation more critical."

[Rok] "We were here before the Alliance, and we will probably get to the Murt before them. But it might not be enough."

[Rok] "They have a stronger force here, so if we aren't fast enough, they might be able to overtake the Murt by force
before we are able to start using it."

[Rok] "Your help is really appreciated here. We could move out any minute now, so stay here and stay alert."

Do you want to share what you now about Murt with Rok?\\
> Tell him what you know\\
> Not yet, I want to check the other options

[Rok] "So that was what you were doing? And the scout fleet, was that you?"

[Rok] "Let's take that discussion later." 

[Rok] "If this is true, this information could tip this entire situation in our favour. We are moving out immediately."

\subsection{Asteroid Belt}

[Rok] "If this information is correct it might buy us the time that we need..."

...

[Rok] "An Alliance scout team! We must shatter them. We can't lead them to the Murt. Bring them down!"

... Level against light Alliance ships ...

\subsection{Murt}

[Rok] "Yes! This must be the asteroid. It looks perfectly ordinary, but our sensors beg to differ."

[Rok] "Let's start the extraction."

...

[Rok] "One of our teams has started the drilling. We have prepared energy cells that are able to handle the Murt."

[Rok] "When they are ready, we will use them to beat down the Alliance. Exciting, exciting!"

...

[Rok] "There is a large Alliance force incoming. We must hold them off for long enough."

[Rok] "This will be the final battle. We can't lose now. Keep it tight everyone."

... Survive a certain time level ...

[Rok] "We have access to the Murt!" 

[Rok] "Quickly, equip those energy cells." 

[Rok] "With those, both the shields and the weapons will overflow with power." 

[Rok] "We will be invincible and immensely powerful."

[Rok] "We can finally pay back for all they have done to us!" 

[Rok] "We can finally get our revenge!"

[Rok] "We can finally eradicate the Alliance!"

... Final overpowered level ... [Featuring desperate messages from the Alliance]

... Fades out into the outro

\end{document}




























