\documentclass[a4paper,12pt]{article}
\usepackage[utf8]
{inputenc}

\begin{document}

\title{Mission 10: The End, Alliance branch - v4}
\author{LinkPactGames}
\date{Novembre 2014}
\maketitle

\section{Summary}

\textit{The player helps the Alliance wringing the Murt from the rebels hands. Military factions
of the rebels are eliminated or dissolved. The war is over. The Aliance is in total control.}

\section{Story points}

o Alliance fleet, Ai: Ai explains the Alliance position\\
\textgreater Asteroid belt: The player and the Alliance move in\\
ox Murt: The Alliance wrings the control over Murt out of the rebels hands\\

\section{Manus}

\subsection{Alliance Fleet}

[Ai] "Long time, no see. It is good to finally see you again."

[Ai] "We have known for a while that the scientists have located a huge quantity of Murt."

[Ai] "They have kept their mouths shut about it. It seems like they don't trust us in the Alliance to be capable
of using it well."

[Ai] "After you kidnapped that scientist the rebels suddenly started gathering a large fleet of ships." 

[Ai] "They abandoned many of their stations, even suddenly abandoning raids against transports."

[Ai] "All of them started travelling here."

[Ai] "This was the signal. They must have suceeded in extracting information about the Murts position from that scientist."

[Ai] "We moved out immediately, but we were unprepared for the speed with which the rebels were able to gather their forces."

[Ai] "They were here before us, and have had more time to scan the asteroids. 

[Ai] "We believe they are able to take control of it any minute now."

[Ai] "It would be a catastrophe. We wouldn't be able to protect the sector anymore." 

[Ai] "They would be able to roam freely, plundering and spreading chaos throughout the sector."

[Ai] "We must stop this at all cost. We are battling them right now, and are closely monitoring their movements in
the asteroid belt."

[Ai] "You will be needed here, so make sure you stay around. This will be a tough one."

Do you want to share information about Murt with Ai?\\
\textgreater Tell her what you know.\\
\textgreater Not yet, I want to check the other options.

[Ai] "What is it you are telling me? You knew all this without telling me until now? Why!"

[Ai] "We don't have time to take that discussion now." 

[Ai] "I'm glad you came to your senses anyway. We should move out immediately."

[Ai] "Maybe there is still time to get to the Murt before the rebels. This could tip everything in our favour."

\subsection{Asteroid Belt}

[Ai] "It must be that asteroid. It is swarmed by rebels, goddammit."

[Ai] "They seem defensive. They don't have access to the Murt yet." 

[Ai] "When they do, they will swarm us like wasps. It will be the end. But there is still time."

[Ai] "Our only option is to hit them with what we've got. Let's break down their defenses before it's too late."

... Eradication level ...

[Ai] "We are almost there. Now, we must take control over Murt. Hit them hard and fast."

... Taking control over Murt-level ...

\subsection{Murt}

A battle is raging around the asteroid, but the Alliance troops hold a small circle around the Murt asteroid.

[Ai] "Yes! We have won! We have control over Murt."

[Ai] "Let's incorporate it into our energy systems. They won't stand a chance."

[Ai] "Let's show them the Alliance's power. Let's show them what happens if you oppose us."

[Ai] "Let's show them who rules this sector."

... Fading out to outro

\end{document}




























