\documentclass[a4paper,12pt]{article}
\usepackage[utf8]
{inputenc}

\begin{document}

\title{Mission 2: Protect the Freighter - v4}
\author{LinkPactGames}
\date{Novembre 2014}
\maketitle

\section{Summary}
\textit{The player joins a small transport-guard to protect an Alliance
transport travelling from Highfence to Soelara. The fleet comes under attack,
and the player helps repelling repeated rebel attacks.}

\section{Story points}
o Highfence, Ai: Welcoming you, giving you mission specifications\\
o Outside Highfence, captain: Ready to take of\\
\textgreater Small talk with captain: Difficulties with rebels\\
\textgreater Small talk with captain: Cargo\\
x Before first attack: brief\\
x After first attack: brief\\
x Before second attack: brief\\
x After second attack: brief\\
x Before third attack: brief\\
x After third attack: brief\\
o Soelara, captain: Arrival, the player is thanked and rewarded\\
\textgreater Hyperspeed, Sair: Hyperspeed and mission\\
o Highfence, Ai: Job well done, future

\section{Manus}

\subsection{At Highfence}

A young woman greets you. She looks at you calmly. 

[Ai] "So you are the new pilot, nice to meet you. I am Ai, and I am currently
responsible for the military operations around this planet."

[Ai] "Berr seemed very satisfied with your help on Border Station. He insisted
that put your skills to use."

[Ai] "Actually, your timing is perfect. We have an important transport heading
for Soelara that is almost ready to leave."

[Ai] "This transport is of particular interest to us. We want to make sure that it is well protected."

[Ai] "Would you help us protect the freighter and its cargo?"

-" I would be happy to help."
\textgreater Great! The captain is waiting outside. He and the rest of the escort
are ready to leave at any moment.

- "Let me think about it."
\textgreater I understand that. I don't think we are able to leave without higher
security, so please don't take too long.

\subsection{Outside Highfence}

[Captain] "You look quite lost. How can I help you?"

[Captain] "..."

[Captain] "You are here to help me, you say?" 

[Captain] "I guess that it won't hurt with an extra ship. Make sure you don't get in the way for the other
escort ships.."

[Captain] "We don't have time to wait for any longer. Let's leave now. Make sure to follow
us closely."

\subsection{Travelling to Soelara}

[Captain] "This path used to be safe. Some years ago I could travel here with minimum protection."

[Captain] "The rebels kept to their base, close to Lavis. I think only Lavis ever had problems with them."

[Captain] "Lately they've started to become increasingly present in all parts of the sector
despite the Alliance efforts to keep them away."

[Captain] "It will take ages to unload all of this cargo." 

[Captain] "I hope that I'll get at least a few hours of solid sleep before tomorrow's 
transport to New Norrland."

[Other escort ship] "There are rebels incoming! Prepare yourselves!"

[Rebel ship] "Surrender the cargo peacefully, or we'll retrieve it from
your scattered remains!"\\

... The rebels attack ...\\

[Captain] "Moronic assholes! What are they thinking? That we would just hand over our cargo,
and then carry on happily?" 

[Captain] "Let's hope that we won't see more of them."

[Sair] "Look, there is another group of rebels on its way. It looks like
their heavier ships have arrived. Be careful!"

[Rebel ship] "We have no mercy for those who destroy our people. 
Prepare yourselves!"

... The rebels attack again ...

[Captain] "How can they think they are doing any good for anyone?" 

[Captain] "They are killing the people who actually struggle to get the sector to go around."

[Captain] "The sector is definitely better off without them."

[Captain] "We are almost there now. It looks like we will avoid further attacks."

\subsection{Arrived at Soelara}

The captain turns to you. He looks tired and relieved. 

[Captain] "That was a close one. We might not have been able to make it without your help. 
Thank you."

[Captain] "We are travelling with samples of a mineral called Murt. The mineral seems to be of great
interest both for the Alliance and the rebels."

[Captain] "You should have your reward. Here is the salary as promised."
 
[Captain] "Also, I saw that you weren't using a shield on the way here."

[Captain] "You can use this Regular Shield. It might not be the best, 
but definitely better than having no shield."

[Captain] "You should return to Ai at Highfence. There is always work that needs to be done these days."

[Captain] "You have been permitted to use the Beacon outside to quickly travel back to Highfence. 

[Captain] "You will be able to use them to quickly travel to locations you have visited before." 

[Captain] "It usually comes to a cost though. We don't have much resources."

The captain salutes you. "Enough chit-chatting. Go now. Stay safe."

\subsection{Travelling back to Highfence}

[Sair] "We should use the Beacon he mentioned. I believe it is that circular
structure over there."

[Sair] (During travel) I have never experienced this before. How interesting.

[Sair] It is only possible to use for transporting small ships like ours.

\end{document}













