\documentclass[a4paper,12pt]{article}
\usepackage[utf8]
{inputenc}

\begin{document}

\title{Mission 8: Beginning Of The End - v3}
\author{LinkPactGames}
\date{October 2014}
\maketitle

\section{Summary}

\textit{The player travel to retrieve technology that can be used to conceal the Murt meteorite.
When arriving at the location of the technology Sair realize that it is too late. The mission can no
longer be completed.}

\section{Story points}

\textgreater Travel to coordinate, Sair: Database information\\
o Coordinate, Sair: Comment\\
\textgreater Travel to meteor belt, Sair: Realization

\section{Manus}

\subsection{Travelling to coordinate}

[Sair] "Ente's logic seems to hold." 

[Sair] "This energy source would be a significant asset in restoring this sector."

[Sair] "Also, its power must be handled with care. Otherwise, it will lead to more destruction than good."

[Sair] "The best course of action is definitely to hide the Murt."

[Sair] "We should hurry. If Ente leaks... This would quickly get out of hand."

\subsection{At the coordinate}

[Sair] "This must be it."

[Sair] "The place seems to be abandoned though..."

[Sair] "Last time we were here the area were swarmed with Alliance ships. What's going on?"

[Sair] "This must be the radar-distortion device. Let's leave now."

\subsection{Leaving the coordinate}

[Sair] "We have incoming messages!"

[Ai] "Where are you? You are needed urgently."

[Ai] "A huge rebel fleet is heading towards an asteoid belt outside New Norrland." 

[Ai] "We believe that it has something to do with the Murt. They must have managed to extract something from that scientist." 

[Ai] "We didn't anticipate how quickly they would react, and they are so many.." 

[Ai] "We are gathering what ships we can at the location X. You should abandon all current missions and travel there
immediately. Over and out."

...

[Sair] "It seems like Ente leaked after all. This is not good."

[Sair] "They don't know the exact location though. We still have a small lead." 

[Sair] "If we get there before they start scanning the belt we might still manage to hide it. Let's go now."

...

[Sair] "Another message..."

[Rok] "We need your help." 

[Rok] "The chat with the scientist guy provided us with some really interesting information." 

[Rok] "According to him there is a huge gathering of Murt somewhere in an asteroid belt outside New Norrland. We are travelling there right now to investigate."

[Rok] "The Alliance seems to have picked up on it too. We need to hurry." 

[Rok] "We are gathering close to the belt. You should travel there immediately. See you there."

...

[Sair] "Interesting situation. We should hurry. It's might be already be too late."

\end{document}




























