\documentclass[a4paper,12pt]{article}
\usepackage[utf8]
{inputenc}

\begin{document}

\title{Mission 9: The End - v1}
\author{LinkPactGames}
\date{October 2014}
\maketitle

\section{Summary}

\textit{The player travels to the asteroid belt. Sair provide further information on the way.
They realise that the original plan can't be executed, and that it is up to them to choose.}

\section{Story points}

\textgreater Travelling to the asteroid belt, Sair - Thinking and radio interceptions\\
o Asteroid belt, Sair - Mission fail, thoughts on what to do next

\section{Manus}

\subsection{Travelling to coordinate}

[Sair] "It looks like both the rebels and the Alliance has started scanning the asteroid belt. We will not be
able to carry out our initial plan."

[Sair] "So. Summarizing the situation."

[Sair] "Both rebels and the Alliance knows about the Murt asteroid."

[Sair] "The rebels roughly knows it whereabouts, and the Alliance knows that the rebels knows."

[Sair] "Both factions want to claim the energy source, and use it for their purposes."

[Sair] "If the rebels get control over it, they will use it to fight back against the so called 'Alliance oppression',
throwing the section into a prolonged conflict."

[Sair] "With the Murt, they would probably win. It is highly uncertain how the sector would look with them in control."

[Sair] "If on the other hand the Alliance get control over it, they will use it to subdue the rebels in the sector."

[Sair] "They would succeed, and could then assert total control over the sector. They could ensure pease, and they
could ensure that they stay in power. People would live according to their rules."

[Sair] "A final, desperate, alternative is to destroy the Murt itself."

[Sair] "According to the scientists information hub, it is unstable in its nature. If we put it under intense fire, it would
probably start a chain reaction leading to an enourmous explosion eradicating everything in the asteroid belt, and probably
eradicating large parts of the New Norrland population."

[Sair] "This would also mean that the people of the sector wouldn't be able to use the Murt at all."

[Sair] "Status quo is upheld. But what kind of status quo?"

[Sair] "We can use our information to help either faction, or to take it in our own hands, destroying the Murt."

[Sair] "I can't calculate this. What is the best path? What should we do?"


\subsection{Arrival at Asteroid belt}

[Sair] "We are here. 

[Sair] "This one is up to you. We should speak to the rebels and the Alliance fleet, to see what they think about the
situation. Then decide if you want to help either of them, or if we should go ahead on our own."

\end{document}




























