\documentclass[a4paper,12pt]{article}
\usepackage[utf8]
{inputenc}

\begin{document}

\title{Endings - v1}
\author{LinkPactGames}
\date{October 2014}
\maketitle

\section{Rebel ending}

After that the rebels took control over Murt, they intensified their raids against the Alliance.
Soon they controlled New Norrland, Lavis and much of the interspacial territory.
The Alliance was initially paralyzed, losing battle after battle. But after a while they started
putting up harder resistance.
The rebels became the stronger faction, but as their power grew they became more and more fractured.
Soon the rebels splitted in three different factions, all with different beliefs about how to rule the system.
The war went on for a long time.\\

At the same time, the rebels and the Alliance managed to agree on keeping a no-war-zone around Peye.
There, research could focus on how to utilize the Murt for good. They managed to create technology that
could yield food for millions of people.\\

You and Sair continues to travel the sector up until today, trying to impact lives for the better.
Sometimes you wonder if you made the best choice. You will never know. 

But you will always know, that you did your best.\\

The End

\section{Alliance ending}

After that the Alliance got Murt under their control they slowly started stablizing the sector part by part.
The rebels initially put up fierce resistance, throwing whatever they had against the Alliance force, but they
soon realized that it was in vain. People started leaving the rebels, quicker and quicker, getting back to their lives.
The Alliance eliminated the remaining rebel fleets that put up resistance.\\

After that they squelched the rebels for good they organized policing forces over the entire sector that should
make sure that events like this would never happen again. They started controlling the information flow of the sector.
It was peace, but it was a forced peace.\\

At the same time, Peye was let to start researching how to use Peye for good. Together they managed to create
technology that could yield enough food to sustain millions of people. People weren't starving anymore.\\

You and Sair continues to travel the sector up until today, trying to impact lives for the better.
Sometimes you wonder if you made the best choice. You will never know. 

But you will always know, that you did your best.\\

The End

\section{Burn ending}

[Sair] "Do you see anything? Do you feel anything?"

[Sair] "I think this is the end. I'm going out soon."

[Sair] "Do you think we did the right choice?"

[Sair] "..."

[Sair] "I guess we'll never know."

[Sair] "But we did our best."

[Sair] "Goodbye. It was nice travelling with you."

[Sair] "..."

\section{Coward ending}

The great explosion that followed eradicated large parts of both the rebel's and the Alliance's fleets, and scarred New Norrlands
surface rendering it unhabitable. People fled New Norrland and spread to the other parts of the sector. People starved, but was at the
same time joined in their efforts of doing the best best they could of the situation.\\

After a while, both the Alliance and the rebels started to recover. Soon the rebels started to raid transports again, and the Alliance
started to claim their interests around the system. This time though, the people of the system joined in an effort to end the war.
They were tired of both the rebels and the Alliance. Finally the rebels and the Alliance started listening, and started pulling back their forces.
It wasn't permanent, but the sector found a sort of temporary peace.\\

You and Sair continues to travel the sector up until today, trying to impact lives for the better.
Sometimes you wonder if you made the best choice. You will never know.\\

But you will always know, that you did your best.\\

The End

\end{document}