\documentclass[a4paper,12pt]{article}
\usepackage[utf8]
{inputenc}

\begin{document}

\title{Mission 9: The End - v4}
\author{LinkPactGames}
\date{Novembre 2014}
\maketitle

\section{Summary}

\textit{The player travels to the asteroid belt. Sair provide further information on the way.
They realise that the original plan can't be executed, and that it is up to them to choose.}

\section{Story points}

\textgreater Travelling to the asteroid belt, Sair - Thinking and radio interceptions\\
o Asteroid belt, Sair - Mission fail, thoughts on what to do next

\section{Manus}

\subsection{Travelling to coordinate}

[Sair] "Both the rebels and the Alliance are already scanning the asteroid belt. We will not be
able to carry out our initial plan."

[Sair] "What should we do now? What can we do now?" 

[Sair] "I need to process this information further."

...

[Sair] "So. Summarizing the situation."

[Sair] "Both rebels and the Alliance know about the Murt asteroid."

[Sair] "The rebels roughly know it whereabouts, and the Alliance knows that the rebels know."

[Sair] "If the rebels get control over it, they will use it to fight back against the Alliance."

[Sair] "With the Murt, they would probably win in the end. It is highly uncertain how the sector would look with them in control."

[Sair] "If on the other hand the Alliance get control over it, it will use it to subdue the rebels in the sector."

[Sair] "They would succeed, and could then take total control over the sector." 

[Sair] "It would probably mean peace, under their control. People would have to live according to their rules."

...

[Sair] "Another, desperate, alternative is to destroy the Murt itself."

[Sair] "It is unstable. If we put it under intense fire, 
it would start a chain reaction leading to an enormous explosion."

[Sair] "This would eradicate everyone in the meteor belt, and probably scar New Norrland badly."

[Sair] "It would also destroy something that could be used to help the people of this sector."

[Sair] "Status quo is upheld. But what kind of status quo?"

...

[Sair] "They still don't know the exact location of Murt. Our information could be very
useful for any side."

[Sair] "Should we try to help either the rebels or the Alliance?"

[Sair] "Or should we try to take it in our own hands? Destroying the Murt."

[Sair] "I can't calculate this. What is the best path? What should we do?"


\subsection{Arrival at Asteroid belt}

[Sair] "We are here. 

[Sair] "This one is up to you." 

[Sair] "We should speak to the rebels and the Alliance fleet, see what they think about the
situation."

[Sair] "You must decide if you want to help either of them, or if we should go ahead on our own."

\end{document}