\documentclass[a4paper,12pt]{article}
\usepackage[utf8]
{inputenc}

\begin{document}

\title{Mission 5: Retaliation - v4}
\author{LinkPactGames}
\date{Novembre 2014}
\maketitle

\section{Summary}

\textit{The player is sent to help retrieving important cargo from an
Alliance freighter ship. The mission is successful, and the
players reputation among the rebels is solidified.}

\section{Story points}

o Rebel station, Rok: Warmly welcomed. Sent on retaliation mission.\\
\textgreater Outside station, Ai: Interaction about the coming mission.\\
ox Ambush location, rebels: Small talk. Ambush, and retreat.\\
\textgreater After ambush, Sair: Brief comment.\\
o Rebel station, Rok: Happy with result. Come back for more missions.\\

\section{Manus}

\subsection{Arriving at Rebel Station}

Rok turns to you with a wide smile. 

[Rok] "Friend! Welcome! I am very glad to have you here. We need people like you.
People that aren't afraid to do what must be done."

[Rok] "The people here are poor and frustrated with how the Alliance keeps using its strength
to exploit us." 

[Rok] "We need more skilled pilots to be able to fight back. Like you!" 

[Rok] "And I'm sure your insight into the Alliance will prove to be very useful..."

[Rok] "Actually, we need your help right now." 

[Rok] "We are planning to raid a transport travelling between Soelara and Fortrun which
we believe carries a particularly large batch of Murt."

[Rok] "Have you heard about Murt? It is said to be the energy source of the future."

[Rok] "Both us and the Alliance are looking into it. The scientists on Peye are also researching it,
but they are very restrictive in what information they share."

[Rok] "It could be the single factor that determines the future path of the sector. We must
do what we can to prevent the Alliance from gaining further insight into it."

[Rok] "I will mark the coordinates for the attack on your map. You will meet the rest of the
fleet at that location."

[Rok] "Some of us are still sceptical of your presence here. This might be
the chance to prove where your true allegiance lies."

\subsection{Outside station}

[Ai] "...They are planning an attack on the freighter?" 

[Ai] "It is surprising that they know about the transport. They must have more insiders than we know about..."

[Ai] "I will look into it. You should participate in the raid as planned. 

[Ai] "You can't do anything erratic now. I will see what I can do about the content of it."

\subsection{Ambush location}

[Rebel] "So! You are the new cape-turner."

[Rebel] "Heard you worked for the Alliance for a while, but got cold feet?" 

[Rebel] "I guess they aren't as pretty as they try to look. Only caring about the rich. 
Leaving us poor to starvation."

[Rebel] "You are very welcome. Your help is appreciated."

...

[Rebel] "Do you prefer ranged weapons like Ballistic Laser, or close combat
weapons like Spread Bullet?" 

[Rebel] "You know, if you ask me weapons like Ballistic Laser and Beam
are for meaklings, afraid of taking a few hits."

[Rebel] "I hope I have enough money to buy a proximity laser one day. That would be fantastic."

...

[Rebel] "Lately, the Alliance has made a lot of development on its stealth technology."

[Rebel] "The fleet protecting the freighter might have some of those ships. 

[Rebel] "Keep your eyes sharp. The ships are not invisible, but very hard to see!"

...

[Rebel] "I can see them on my radar now. 

[Rebel] "Remember, we are only here for the cargo. Hit it fast and hard, and then leave."

[Rebel] "No need to hold back though, hit those bastards where it hurts!"

[Rebel] "Here it goes, for the people!"

... Mission ...

[Rebel] "Surrender the cargo peacefully, and you will come to no harm..."

[Alliance] "Do you believe that bullshit yourselves? You are going down with us."

...

[Rebel] "We've got the cargo. Pull out! Pull out!" 

[Rebel] "Their reinforcements must be on their way. We'll meet at the base."

\subsection{Travelling back to Rebel Station}

[Sair] "I don't like those high-odds operations. If the Alliance hangar ships would have
arrived a bit earlier we would have been done for..."

[Sair] "We threw the right side of the dice this time." 

[Sair] "We should meet Rok at the rebel base, see what he has to say."

\subsection{Back at the Rebel Station}

Rok greets you. 

[Rok] "I heard it was a close call. But what's important is that you got out, and
that you have the cargo." 

[Rok] "Let's see if it proves to be as valuable as we hope. They are searching the cargo right now."

He looks thoughtful. 

[Rok] "I don't like how the Alliance have been acting lately." 

[Rok] "The transport seemed to be of high importance for them. But if the cargo was really important for them, the escort security
should have been even higher."

[Rok] "This didn't seem like a crucial piece for them, and that worries me.."

[Rok] "You should get some rest while you can. Come back then. 

[Rok] "Hopefully they'll manage to extract some useful information about the cargo, 
maybe a lead on what we should do next."

\end{document}













