\documentclass[a4paper,12pt]{article}
\usepackage[utf8]
{inputenc}

\begin{document}

\title{Mission 4: Infiltration - v1}
\author{LinkPactGames}
\date{October 2014}
\maketitle

\section{Summary}

The player is sent to infiltrate the rebels. The player provide
the rebels with information about an imminent attack. The allied
fleet is caught in an ambush, and there the player joins the rebels.

\section{Story points}

o Fortrun, Ai - Told about mission and reasoning about it\\
o Outside Fortrun, Sair - Brief discussion on the subject\\
\textgreater Travel, Sair - Brief comment\\
o Location outside solar system, Rebel Rok - Information leak\\
\textgreater Travel, Sair - Brief comment\\
o Attack location, fleet - Sceptical discussion, attack, talk with rebels\\
\textgreater Travel, Rok - Aftertalk

\section{Manus}

\subsection{At Fortrun}

Ai turns to you with a grave look on her face.
"I just returned from a meeting with the Alliance top council.
We have a great favour to ask from you. But first I should introduce you
to the situation."

"You have heard about our research on the mineral Murt. We have made significant
progress lately, and if we just find it in greater quantities it could very well
become a crucial factor in raising the sector on its feets again."

"But that is not all. If someone with the right knowledge would gain access to
larger quantities of Murt, this would give the owner an immense power. It could
be used to power the ships and houses of the sector, to power our green houses.
It could also be used as a weapon, powering lasers, shields and bombs to an
almost unimaginable level."

"We have reasons to believe that there is such a source of Murt. We also have
reasons to believe that the rebels know about this. If they were to gain access to it, it would grant them power greater than that of the entire Alliance combined. We must stop them from gaining access to this mineral at any cost."

"It is here you comes in. We need an insider. Someone they can trust, who can
provide us with insight in what they know and what they plan."

"You are a skilled and trusted pilot. You is also an unknown for them. You
don't have a reputation. You could be one of the rats, leaving Alliance for
the gold and green forests that the rebels promise."

"Our plan is to let you leak crucial information about a coming attack against
one of their outposts near Lavis. You will warn them and you will join them
during the attack. You will be sent their together with a group of suspected
rats. You and the rebels will help us get rid of them, and at the same time
lay a foundation of trust in you."

"I have set up a meeting with a lower rebel at coordinates (X,X). You should
travel there immediately, and hand him this file. Then, you will travel to the
outpost and join the attack fleet. I will provide you with the exact coordinates
after the meeting."

She looks at you seriously. "Good luck, friend. I will stay in touch."

\subsection{Outside Fortrun}

[Sair] That was unexpected. But it might be the logical choice.
Let's go meet that rebel person.

\subsection{Travelling to meeting location}

[Sair] You know. This might be the last moment of stillness we get in a while.
You should take a moment to appreciate it.

\subsection{Meeting Rok}

A young man with a fierce look appears on your display.

[Rok] "So you came after all. And you seems to have no company. Brave!
Stupid, and brave.. Let's get to it. You had information. Sent it over."

He speaks with a quite harsh voice. It sounds like he isn't as confident with
the situation as we tries to appear. You transfer the information.

[Rok] "..."

[Rok] "... Why would you tell us this. A change of heart you say? I have
difficulties believing you. But I also have difficulties understanding you."

[Rok] "..."

[Rok] "I will leave you now. If this is true, and you follow the plan through,
there will be a place for you by us, the Liberators. If not... I will make
sure you regret this meeting."

[Rok] "Bye for now"

The screen goes blank, and the small group leaves silently.

[Sair] That was tense. It wouldn't have been illogical for him to shoot us
down at the spot.

[Ai] "..Did it go as planned? Fantastic! Now, join the attack fleet at coordinate
(X, X). There is no looking back now. This might be our only chance to get a
grip of the rebels."

\subsection{Travelling to attack location}

[Sair] "Remember. Even if the Alliance fleet we will join is mainly quite
unexperienced pilots, they will have better equipment than most of the rebels
we have faced this far. Be careful."

\subsection{Meeting attack fleet}

A rough and seemingly annoyed man appears on your display.
[Attack fleet leader] "You are late, scum. This is not a walk in the park.
I will not watch your back if you not are able to follow orders."

He directs his next message to the entire fleet.
[AFL] "I will not hold a fucking inspirational speech for you. Do your job,
and we can go home. I don't know what they are fucking thinking, sending us here.
I guess someone has to do their dirty job."

[AFL] "We will try to make this as quick as possible. Go in, destroy everything,
and leave. Make sure they don't have time to forward the message, or we will
be swarmed on our way back."

[AFL] "Let's move out. Don't fall behind."

\subsection{Attack on Alliance}

... Mostly empty level ...

[AFL] "What is this? The station is abandoned.."

Rebels appear on your radar.

[AFL] "What? It is a trapped. Someone has ratted us out. Pull back. Pull the fuck
back!"

Rok appears on your display.
[Rok] "You came here after all. Well done. Now, let's finish this."

[Sair] "Let's get this over with."

... Attack on Alliance with the rebels ...

[AFL] "Are you fucking kidding me? What are you doing, idiot?"

[AFL] "What did they promise you? Gold and happiness? Oh, your dreams
will turn to ashes. You will regret this. You will really reg.."

[Rok] "Don't let them escape. Let's pay back for all that they have done to us."

The connection was aborted. The level begins, and ends.

Rok appears, looking relieved and excited.
[Rok] "Amazing job my friend! We really got them there. They will think one time
or two before attacking us again."

[Rok] "We would not have been able to do it without you. We really appreciate it.
A small, but significant step towards the peoples liberation. Thank you."

[Rok] "Travel to the coordinates (X,X). There you will find our base. I will tell
you more about us, and you will tell us more about you. You will get a place
by us Liberators. You will not regret this choice. See you later!"

\subsection{Travel with rebels to base}

[Ai] "It went as expected? Good. I feel bad for putting you through this,
but it was a necessity. I'm sure you understand."

[Ai] "Don't get fooled by them. Many of them themselves believe that they
are standing for good and justice. Remember all the people they plundered and
murdered around the system."

[Ai] "I wish you best of luck. Contact me immediately when you find anything useful."

..connection ended..

\end{document}













