\documentclass[a4paper,12pt]{article}
\usepackage[utf8]
{inputenc}

\begin{document}

\title{Mission 8: Beginning Of The End - v1}
\author{LinkPactGames}
\date{October 2014}
\maketitle

\section{Summary}

\textit{The player travel to retrieve technology that can be used to conceal the Murt meteorite.
When arriving at the location of the technology Sair realize that it is too late. The mission can no
longer be completed.}

\section{Story points}

\textgreater Travel to coordinate, Sair - Database information\\
o Coordinate, Sair - Comment\\
\textgreater Travel to meteor belt, Sair - Realization

\section{Manus}

\subsection{Travelling to coordinate}

[Sair] "Ente's logic holds. This energy source might be the one and only chance of lifting this sector from
its ongoing decline. Also, its power must be handled with care, or it will lead to more destruction than good."

[Sair] "The conclusion of this is that the best course of action must be to hide source for the times being. We should make sure that
the Murt becomes hidden, and that it isn't revealed until it can be handled."

[Sair] "We should travel there immediately. As Ente said, it is only a matter of time until the rebels or the Alliance manage to localize the Murt."

[Sair] "According to the data, the technology is being developed at another outpost close to Peye. The security is much lower there though,
so it shouldn't be a problem to slip through."

[Sair] "Let's go now."

\subsection{At the coordinate}

[Sair] "We are here. It seems to be abandoned though. Something must be wrong. Last time we were here the area were swarmed with Alliance ships. 
Now, there is almost nothing."

[Sair] "This must be the radar-distortion device. Let's leave now."

\subsection{Leaving the coordinate}

[Sair] "We have incoming messages!"

[Ai] "Where are you? You are needed urgently. A huge rebel fleet is heading towards a asteoid belt outside New Norrland. We believe that
their actions are related to the Murt. We are gathering what ships we can at the location X. You should abandon all current missions and travel there
immediately. Over and out."

[Sair] "It seems like Ente leaked after all.." 

[Sair] "They might not know the exact location or the Murt though, so we still have a small lead. Let's bring the hiding device.
If we get there before they start scanning the belt we might still manage to hide it. Let's go now."

[Ente] "We need your help. The chat with the scientist guy provided us with some interesting information. He belive that there is a huge gathering
of Murt somewhere in an asteroid belt outside New Norrland. We are travelling there right now to investigate."

[Ente] "The Alliance seems to have picked up on it too, so the time is really short. We are gathering close to the belt. 
You should travel there immediately. See you there."

[Sair] "Interesting situation. We should hurry. It's might be already be too late."

\end{document}




























