\documentclass[a4paper,12pt]{article}
\usepackage[utf8]
{inputenc}

\begin{document}

\title{Mission 5: Infiltration - v1}
\author{LinkPactGames}
\date{October 2014}
\maketitle

\section{Summary}

\textit{The player is sent to help retrieving important cargo from an
Alliance freighter ship. The mission is successful, and the
players reputation among the rebels is solidified.}

\section{Story points}

o Rebel station, Rok - Warmly welcomed. Sent on retaliation mission.\\
\textgreater Outside station, Ai - Interaction about the coming mission.\\
ox Ambush location, rebels - Small talk. Ambush, and retreat.\\
\textgreater After ambush, Sair - Brief comment.\\
o Rebel station, Rok - Happy with result. Come back for more missions.\\

\section{Manus}

\subsection{Arriving at Rebel Station}

Rok turns to you with a wide smile. "Friend! Welcome! I am very glad to
have you here. We need people like you. We have attracted a lot of people
with different backgrounds lately." 

"Most of the people here are poor and frustrated with the
Alliance exploiting them. We need more
skilled pilots. Like you! And you have insight in the ways of the Alliance.
I'm sure that knowledge will prove to be very useful..."

"Actually, we would need your skills right now. We are planning to raid a
transport travelling between Soelara and Fortrun. Our intel tells us they are
gathering a particularly big guard for it. Those transports often contains
samples of the mineral Murt."

"Have you heard about it? I don't know how much of it that is true, but it
is said to be the energy source of the future. Of course both we and the
Alliance are looking into it. The scientists on Peye are also researching it,
but they are very restrictive in what information they share."

"If it lives up to its reputation it could be the factor which finally lets
us liberate the sector from the narcissistic Alliance, and finally puts
the power back at the people."

"Nevertheless. Those samples of Murt are crucial for our insight into the Murt.
This mission seems to be a tough one, so we need all the help we can get."

"I will mark the coordinates for the attack on your map, and tell the others
that you will join them."

"Some of the rebels are still sceptical of your presence here. This might be
the chance to prove where your true allegience is."

\subsection{Outside station}

[Ai] "...They are planning an attack on the freighter you say? It's surprising
they know about the transport, they must have more rats than we know about...
I will look into it."

"You should participate in the raid as planned. You can't
do anything erratic now. I will see what I can do about the content of it."

\subsection{Ambush location}

[Rebel] "So you are the new cape-turner. Heard you worked for the Alliance
for a while, but got cold feet? I guess they aren't as pretty as they try
to look. Only caring about the rich population. Leaving us poor to starvation.

You are very welcome. Your help is appreciated."

[Rebel] "Do you prefer ranged weapons like Ballistic Laser, or close combat
weapons like Spread Bullet? You know, if you ask me weapons like Ballistic Laser and Beam
are for meakling, afraid of taking a few hits.
I hope I have enough money to buy a proximity laser one day. That would be fantastic."

[Rebel] "Lately the Alliance has made a lot of development on their stealth technology.
The fleet protecting the freighter might have some of those ships. Keep your eyes sharp.
They are not invisible, but very hard to see!"

[Rebel] "I can see them on my radar now. Everyone, prepare yourself. Remember, we are
only here for the cargo. Hit it fast and hard, and then leave."

[Rebel] "Here it goes, FOR THE PEOPLE!"

... Mission ...

[Rebel] Surrender the cargo peacefully, and you will come to no harm...

[Alliance] Do you believe that yourself, bastards? You are coming down with us.

...

[Rebel] We've got the cargo. Pull out! Pull out! Their reinforcements must be on their way.
We'll meet at the base.

\subsection{Travelling back to Rebel Station}

[Sair] "I don't like those high-odds operations. If the Alliance hangar ships would have
arrived a bit earlier...

We threw the right side of the dice this time. We should meet Rok at the rebel base, 
see what he has to say."

\subsection{Back at the Rebel Station}

Rok greets you. "I heard it was a close call. But the main point is that you got out, and
that you have the cargo. Let's hope it proves to be as valuable as we hope. They are analyzing
the mineral in the laboratorium right now."

He looks thoughtful. "I don't like how the Alliance have been acting lately. The transport seemed
to be of high importance for them. But if the cargo was crucial for them, the escort security
would have been even higher. This didn't seem like a crucial piece for them, and that worries me.."

"You should get some rest while you can. Come back then. Hopefully they manage to extract some
useful information about the cargo, maybe a lead on what to do next."

\end{document}













