\documentclass[a4paper,12pt]{article}
\usepackage[utf8]
{inputenc}

\begin{document}

\title{Mission 10: The End, On Your Own - v1}
\author{LinkPactGames}
\date{October 2014}
\maketitle

\section{Summary}

\textit{The player decides to take it into your own hands. The player travels to the Murt, avoiding
rebels and Alliance fleets. At the arrival the player either sets Murt on fire, or flees, leaving everyone else behind.}

\section{Story points}

o Asteroid belt - Sair reasons about the situation\\
\textgreater x - Travelling to the Murt, avoiding two fleets\\
o Murt - Reasoning on spot -> Player is prompted to choose again\\
\textgreater \textgreater Burn Ending\\
\textgreater \textgreater Coward Ending

\section{Manus}

\subsection{Asteroid belt}

[Sair] "It is possible that we could manage to destroy the entire Murt meteorite before anyone else
reaches the location."

[Sair] "It would mean that we keep Murt out of the hands of both the Alliance and the rebels, avoiding one faction
overpowering the other and asserting control over the sector."

[Sair] "It would also mean that we destroy something which rightfully belongs to the people of this sector."

[Sair] "A possible future. It would kill the entire Alliance- and rebels-fleet that are here, and likely burn away this side of New Norrland."

[Sair] "We wouldn't be thanked for that. It wouldn't end the conflict. But at the same time it would prevent the Murt
from being misused to kill and control."

[Sair] "Do you think this is the best of the worst choices?"

> "Yes. Let's go ahead and destroy the Murt."
> "I have to think a bit more about this."

[Sair] "Well then, it is decided. Let's go!"

\subsection{Travelling to Murt}

[Alliance] "Identify yourself! Are you a rebel ship? I'm sorry. We can't let you continue."

... Avoidance The Alliance level ...

[Sair] "Well done. The area seems to be swarmed by both Alliance and rebel scouts keep your guard up."

[Sair] "A rebel scout fleet is incoming. Let's try to slip through!"

... Avoid The Rebels level ...

\subsection{Murt}

[Sair] "Finally, we made it through! It appears we managed to make it here before the others."

[Sair] "To end this, just open fire. Heat the asteroid until it takes fire. Burning it. Burning it all."

[Sair] "Are you ready to do it? Are you sure this is the way to go? I still don't know."

[Sair] "Maybe we are trying to be more than we are. Maybe we are removing the systems last hope in vain."

[Sair] "Or maybe this will save the entire sector from sinking further into war and chaos, fueled by the immense power
of Murt."

[Sair] "What do you say. Should we do it? We can still back away, escaping it all."
- Let's do it. Let's destroy the Murt.

[Sair] "Alright then. It is decided."

[Sair] "No backing down now. Let's open fire!"

... Last level, setting a meteor on fire ...

... Fading out, displaying the explosion, before the after text comes in

- This is not our choice to make. Let's move out.

[Sair] "You might be right. I don't know. It is decided now anyway. Let's move out."

[Sair] "Let's hurry. Who knows what will happen when they get here."

[Sair] "They are opening fire around the Murt. It might very well lead it exploding anyway!"

[Sair] "Let's GO!"

... Fading into cutscene where the asteroid belt explodes ...

\subsection{Ending -  Burn}

[TO BE WRITTEN]

\subsection{Ending -  Coward}

[TO BE WRITTEN]

\end{document}




























