\documentclass[a4paper,12pt]{article}
\usepackage[utf8]
{inputenc}

\begin{document}

\title{The Sun Will Go Out - Portrait specifications}
\author{LinkPactGames}
\date{October 2014}
\maketitle

\section{Overview}

\subsection{Central characters}

These are unique characters or particular interest for the main story. Many of them
are present in large parts of the main story. Those are the ones of highest priority,
for which portraits are most important.

\begin{itemize}
	\item{Sair}
	\item{Berr}
	\item{Ai}
	\item{Rok}
	\item{Ente}
	\item{Alliance commander}
\end{itemize}

\subsection{Generic characters}

Genres of characters that appear several time during the game in different persons.
There are for example several fleet captains in the game with different personalities and backgrounds,
but they are all 'fleet captains'. Those are of lower priority than the central characters, but portraits of these 
would still be really beneficial for the atmosphere of the game.

\begin{itemize}
	\item{Alliance captains}
	\item{Rebel troop leaders}
	\item{Alliance pilots}
	\item{Rebel pilots}
	\item{Common citizens}
\end{itemize}

\section{Central characters}

\subsection{Sair}

Sair the player's talking ship. Sair is present during the entire game, and is a logical entity
reflecting over the events, and sometimes decides the path for the player.
Even if most people in the sector prefer non-talking ships, they are not uncommon.\\

Sair does not have an apperance in particular, as it is a part of the ship system. Sair does
not have a particular gender. This will probably be the most abstract portrait, and is open for
interpretation. Maybe some kind of 'non-human entity' would be a way to depict it, like a spirit
bound to the ship.

\subsection{Berr}

Berr is a citizen of the space station 'Border Station'. He works for the Alliance and is responsible for
managing the ships around the station. This includes military tasks, but mainly organizing transport
and introducing new pilots to the Alliance. He cares deeply for the station and its people.\\

Berr is a kind and slightly overweight middle aged man. He might have a soft expression, and is probably
not a frequent shaver (but is neither a dedicated beard-wearer). Is not a tidy person. He might or might not
have hair sticking out from his ears.

\subsection{Ai}

Ai is a sub-commander of the Alliance. She travels between different planets and stations that are
under the Alliance's command and mainly organizes their defenses. She is also a skilled pilot, and often
takes part herself in the raids. She is known as non-humorous and serious.\\

Ai is a young-to-middle aged woman, with a calm and serious expression. She is tidy, but does not
focus much on looks. She might or might not have a strict pony tail. Wears uniform.

\subsection{Rok}

Rok is a sub-commander in the rebels. He is an emotional young man with strong morals. He is an overall
intense person, both as a friend or as an enemy. He is leading a small rebel fleet which often takes part
in high-risk operations like raiding guarded transports.\\

Rok is a quite vain young man. He likes to style his hair so that it looks untidy in a controlled fashion.
He might or might not have a small stylistic beard. Might be considered good-looking by others
than himself.

\subsection{Ente}

Ente is an old scientist who have spent his entire life dissecting the world around him. He is overanalytic
and kind. He has a low tolerance for stupidity, and always attempts to do what he thinks is the best
for the people around him.\\

Ente is a quite typical chaotic scientist. An old man with glasses and hair standing in every direction.
He likes to stare analytically at people, and probably does that in his picture.

\subsection{Alliance commander}

The commander is a hardened man with deep wrinkles. He is a person who get things done, and has
zero tolerance for people who mess around. Lives on the Alliance's home planet Fortrun, and has been
the top command for some years. Some say he enjoys it, some say he does it because no one else could
do it better.\\

An old, totally non-humorous man radiating power and control. Is quite thin, with a slightly bony face.
No beard, and very strict haircut. Might or might not bear an appropriate military hat.

\section{Generic characters}

The specifications here will be less specific as the characters are more 'general'. It is preferable
with non-unique characteristics, more representing the 'generic group' the portraits represent.

If you have the energy, it could be nice with both male and female variants of those groups.

\subsection{Alliance captains}

Ordered and strict. Important pieces in getting the sector to work the Alliance's way, and they know it.
They take their job seriously and probably often looks quite woody. Wears uniform.

\subsection{Rebel troop leaders}

Main players of the rebel forces. Less strict than the Alliance captains. 
Are in general a bit more expressive than the Alliance, but still takes their position seriously.

\subsection{Alliance pilots}

Not as passionate about their task as their captain. Less strict, but still tidy. Wears uniform.

\subsection{Rebel pilots}

Often common citizens taking up weapons to fight against what they see as oppression.
They are untidy and angry. They want change.

\subsection{Common citizens}

It's a hard life, being a citizen in this sector. They are still quite content though, but might not
be radiating with happiness. Would commonly need a bath.

\end{document}













