\documentclass[a4paper,12pt]{article}
\usepackage[utf8]
{inputenc}

\begin{document}

\title{Mission 2: Rebels in the meteors}
\author{LinkPactGames}
\date{October 2014}
\maketitle

\section{Summary}
The player joins a small transport-guard to protect an Alliance
transport travelling from Highfence to Soelara. The fleet comes under attack,
and the player helps repelling repeated rebel attacks.

\section{Story points}
o Highfence, Ai - Welcoming you, giving you mission specifications

o Outside Highfence, captain - Ready to take of

> Small talk with captain - Difficulties with rebels

> Small talk with captain - Cargo

x Before first attack - brief

x After first attack - brief

x Before second attack - brief

x After second attack - brief

x Before third attack - brief

x After third attack - brief

o Soelara, captain - Arrival, the player is thanked and rewarded

> Hyperspeed, Sair - Hyperspeed and mission

o Highfence, Ai - Job well done, future

\section{Manus}

\subsection{At Highfence}

A young woman greets you. "So you are the new pilot, nice to meet you!
Bert seemed very satisfied with your help on Border Station. He insisted
that we should put use of your skills."

Actually, you have perfect timing. We have an important transport heading
for Soelara that is ready to leave. We have got intel though that the rebels
might be aware of that this transport is of particular interest for us.
We believe that it won't be any problem, but to be at the safe side we would
like to increase the escort size.

Would you help us? The mission is to help guarding an important transport
that is leaving for Soelara any moment.

- I would be happy to help.
> Great! The captain is waiting outside. He, and the rest of the escort
is ready to leave any moment.

- Let me think about it.
> I understand that. I don't think we are able to leave without higher
security, so please don't take too long.

\subsection{Outside Highfence}

The captain speaks to you. "You look quite lost. How can I help you?"

"..."

"You are here to help me you say?" He eyes you sceptically. "I guess that
it won't hurt at least. Make sure you don't get in the way for the other
escort ships.."

"We don't have time to wait for longer. Let's leave now. Make sure to follow
us closely."

\subsection{Travelling to Soelara}

(While travelling)
"This path used to be safe. For some years ago I could travel here with a
minimum guard to scare away occational plunderers. The rebels kept in the
north. I think only Lavis ever had problems with them then.
Lately they have been becoming increasingly present in all parts of the sector
despite the Alliance efforts to keep them away."

"It will take ages to load of all this cargo. I hope that I'll get at least
a few hours of solid sleep before tomorrows transport to New Norrland."

[Other escort ship] There are rebels incoming! Prepare yourselves!
[Rebel ship] Surrender the cargo peacefully, or we'll retrieve it from
your scattered remains!\\

... The rebels attack ...\\

Captain: "Moronic assholes! What are they thinking? That we just should leave
our cargo to them, and then get on happily? Let's hope that we won't see more of them."

[Sair] "Look, there are another group of rebels on their way. It looks like
their heavier ships have arrived. Be careful!"

[Rebel ship] We have no mercy for those who destroy our people. 
Prepare yourselves!

... The rebels attack again ...

Captain: "I'm awed by how they can think they are doing any good by trying
to kill the people who actually struggle to get the sector go around.
The sector are definitely better of without those."

"We are almost there now, it looks like we won't be further attacked."

\subsection{Arrived at Soelara}

The captain turns to you. He looks tired and relieved. "That was a close one.
We might not have been able to make it without your help. Thank you."

"You should have your reward. Here is the salary as promised. Also, I saw that you weren't using a shield on the way here. This might not be the best, but compared to travel without one it will make a great difference."

"I wish the best of luck for you in the future. You should return to Ai at
Highfence. There are always work that needs to be done those days."

"I talked to the leader around here, and you have been permitted to use the Beacon outside to quickly travel back to Highfence. You will be able to use them to quickly travel to locations you have visited before. It usually comes to a cost though. As you know, the resources are sparse."

The captain salutes you. "Now, enough chit-chatting. Go now. Stay safe."

\subsection{Travelling back to Highfence}

[Sair] We should use the Beacon he mentioned. I believe it is that circular
structure over there.

[Sair] (During travel) I have never experienced this before. How interesting.
I guess it's only possible to use for small ships like ours. Otherwise the
energy cost would be far to high.

\end{document}













