\documentclass[a4paper,12pt]{article}
\usepackage[utf8]
{inputenc}

\begin{document}

\title{Mission 3: Defend Colony - v3}
\author{LinkPactGames}
\date{October 2014}
\maketitle

\section{Summary}
\textit{The rebels have occupied an area on New Norrland. This affects both people in
the vicinity, and the Alliance itself as it interferes with Alliance
mining interests. The player joins an Alliance fleet which successfully
repels the rebels.}

\section{Story points}

o At Highfence, Ai: Sent to Fortrun for important mission\\
o At Fortrun, Ai and Par: Discussion about rebels. Told to participate.\\
o Outside Fortrun, Ai: The fleet takes of\\
\textgreater Travelling to New Norrland: Talking with Ai and others\\
o Outside New Norrland, Ai: Talks to the fleet\\
x Mission: Taking control over the mine\\
o New Norrland, other pilots: Reflection over the situation\\
x Mission: Defending the mine\\
o At New Norrland: Celebrations and civil sceptic input\\
\textgreater Travelling to Fortrun, Sair: brief\\
o Fortrun, Ai and commander: Well done, come back later

\section{Manus}

\subsection{At Highfence}

Ai welcomes you.

[Ai] "Well done! There will be many opportunities for you here."

[Ai] "In fact, I just got the word from the Alliance command at Fortrun that there currently is a crisis on New Norrland."

[Ai] "They told us to gather as many ships as possible and meet at Fortrun immediately."

[Ai] "I will go there now. You should go too. I will see you there."

\subsection{Outside Highfence}

[Sair] "A new mission? Let's leave then."

[Sair] "Fortrun is usually closed for outsiders. I wonder what's going on."

\subsection{At Fortrun}

[Ai] "Come in, join us." Ai waves you to follow her into a crowded room.

The center of attention is an old man with a hard face. You identify him
as one of the Alliance's commanders.

The commander turns to the group. 

[Commander] "Some of you who knows why we have gathered here,  others don't."

[Commander] "Most of you are aware of our crucial Murt-mining operations on New
Norrland." 

[Commander] "This operation is essential for our continued Murt-technology development."

[Commander] "The rebels have managed to take control over the entire mine, and large parts of the surrounding land." 

[Commander] "This is an emergency for both us and the locals on the planet."

The commander stares at the crowd. 

[Commander] "We have gathered all available pilots. We must strike hard and decisively."

[Commander] "We cannot lose this mine to the rebels, and the locals depend on our protection. We
can't let them down."

[Commander] "The fleet leaders have been provided with instructions. They will further them to
their respective fleets".

The commander leaves the room. A worried mumble spreads in the crowd.

[Mumble] "...they have never been so coordinated..."

[Mumble] "...what are they thinking? ...how are the locals doing?..."

Ai turns to you and the rest of her squad. She calmly looks at all of you.

[Ai] "We have to show the rebels that we are still in control. It would be a catastrophy if the largest source of
Murt in the sector falls into their hands." 

[Ai] "Let's strike them down, show them that they cannot be allowed to interfere with the people of this sector."

[Ai] "We will meet outside in a moment. I will give you further instructions when it is time."

Ai leaves the room.

Ai's short speech seems to have improved the mood of her squad. They seem to trust her
judgement. 

Some of them nods approvingly to each other, before silently leaving for their ships.

\subsection{Outside Fortrun}

[Sair] "Something is different with this mission. On the previous missions, the other pilots
seems to have been quite confident about what they were getting themselves into." 

[Sair] "This seems to be new and unknown for most of them. Maybe they feel that the rebels are growing out
of their control. Stay safe."

[Ai] "Everyone is here? Good. Let's go. Don't stray behind."

\subsection{Travelling to New Norrland}

(The different squad members speak with some delay between, during travel)\\

[Squad member1] "..I don't know about this.. One more salary, and I would have had that
Durable Shield."

[Squad member1] "Now I'm stuck with this crappy Basic Shield. It might be a matter of life and death!"

[Squad member2] "..They are getting stronger, but they still have much weaker ships than us. 

[Squad member2] "They don't seem afraid of collateral damage. Keep away from those terrible mines and bombs."

[Squad member3] "..Yeah.. I heard that they have focused on building more explosives."

[Squad member3] "I have heard about ships spitting bombs that generates huge explosions." 

[Squad member3] "I think it is possible to blow up the bombs by firing at them though.."

[Squad member4] "..I wonder how they treat the civilians around the mines. Our command seems mostly worried
about the mine." 

[Squad member4] "There is a quite large city nearby the mine. I hope they are ok..

\subsection{At New Norrland}

[Ai] "It is time. Our task in this operation is to secure the mine to prevent the rebels from destroying it. 

[Ai] "Then, we must hold or positions until the other squads has secured the surrounding area."

[Ai] "Intel tells us they have an increased presence of explosive ships in the area." 

[Ai] "That means bomb ships and mine layers." 

[Ai] "Keep mobile, and make sure you don't get trapped by their mine fields. 

[Ai] "If you do, try to fire your way through."

...

[Ai] "It is time. Focus on getting through. Don't worry about shooting
down more than necessary." 

[Ai] "Let's go."

...Level...

[Ai] "We are through. Now we must hold our position here for long enough."

[Ai] "Another squad is on the way. Keep your focus."

...Level...

[Ai] "The area is under our control. That's a relief. Well done everyone."

\subsection{Travelling to Fortrun}

[Sair] "It seems like someone is trying to get through a broad-cast message."

[Civilian] "...Is this thing working?" 

[Civilian] "I want to tell you wanna-be-heroes, that not everyone here
approves of your presence." 

[Civilian] "You don't care about the civilians, don't you?" 

[Civilian] "All you care about is your mine, your profit, and to make sure you can live your cozy lives at Fortrun."

[Civilian] "People are starving here. Can't you just let us be?"

[Civilian] "The rebels aren't good either, but at least they aren't sucking out our resources under the pre..." 

The connection is abruptly ended.

[Ai] "People here don't realize what we actually do for them."

[Ai] "Someone needs to be in charge to organize the sector and manage the sectors scarce resources."

[Ai] "Would anyone prefer rebel anarchy? Would they?"

...

[Sair] "I have never heard Ai sound so agitated before. Maybe it hit her in a soft spot."

\subsection{At Fortrun}

Ai looks at you with her usual calm face. She seems to have calmed down since the incident on New Norrland.

[Ai] "You did well back there. We suffered very low casualities compared
to the rest of the squads, much thanks to you. You have grown into a skilled pilot." 

[Ai] "You should get some rest. Come back here later. We will have more missions for you."

You and Ai leaves the room. You go back to your ship.

[Sair] "There seems to be a lot going on under the surface here." 

[Sair] "It could be interesting asking around a bit on Fortrun and other planets, to hear what people are thinking. 

[Sair] Anyway, let's get some rest."

\end{document}













