\documentclass[a4paper,12pt]{article}
\usepackage[utf8]
{inputenc}

\begin{document}

\title{Mission 6: In The Name Of Science - v1}
\author{LinkPactGames}
\date{October 2014}
\maketitle

\section{Summary}

\textit{The player is sent on a mission to retrieve a scientist from Peye.
The player has a serious discussion with the scientist, before returning him
to the rebels.}

\section{Story points}

o Rebel Station, Rok - Findings, need to retrieve scentist at Peye\\
o Outside Rebel Station, Sair, rebel - Comments\\
\textgreater To Peye outpost, Ai and Sair, discussing the situation\\
\textgreater x To Peye outpost, slippin' through Alliance outpost - Breaking through\\
o Outpost, Scientist Ente - Speaking with Ente, introducing possible Murt-plan, and Murt
gathering\\
\textgreater x To Rebel Base, attacked fiercely by Alliance\\
o Outside Rebel Station, Ente - Comment\\
o Rebel Station, Rok\\
o Outside Rebel Station, Sair - Comment

\section{Manus}

\subsection{Rebel Station}

Rok speaks. He looks worried. "Welcome back. It is good that you came so quickly."

"We didn't find much Murt in the cargo. It seems like they managed to get it off in time.
on the other hand, we found some interesting conversations in their log system."

"They spoke about a group of scientists living near Peye, who also have been scanning the solar system
for Murt. They have no particular allegience, neither to Alliance or us rebels, but have lately been depending on a small
Alliance fleet for their protection."

"According to the logged conversation it seems like that the scientists have been providing information about
when they found small quantities of Murt to the Alliance. In return they have got a share of the retrieved Murt for their
research, as well as protection."

"Recently though, the information came to a sudden stop. It seems like they have found something which they are unsure
about if they want to share with the Alliance. We don't know what it is they have found out, but it is likely to be related to
Murt."

"Naturally, the Alliance is very upset about this, and is currently pressuring the scientists to share their information. It is
probably only a matter of time before they get what they want."

"That's why we have to act now, as quick as possible."

"We have a name to one scientist that seems to be of high importance - Ente. He has been deeply involved in the Murt
research, and is said to be sceptical of their relationship to the Alliance. He thinks they should be able to share the information
with whoever they think is fit, and strongly dislikes that the Alliance can prevent him from sharing information openly in the sector."

"We want to bring him here, and to have a chat with him. We will send a small group of ships which will try to slip through
the Alliance's defenses around the research station, extract Ente, and return him here."

"The idea is simple, but this will likely be a highly dangerous mission. You should prepare yourself properly. Then meet with the
other's of the fleet who are waiting nearby the rebel base."

\subsection{Outside Rebel Station}

[Sair] "'Bring him here to have a chat with him', that sounds really sinister to me.. We shouldn't let our guards down.
Remember why we are here. We should speak to Ai, but we cannot do it right now when we are so close to the other ships."

[Rebel] "All here? Good. We'll move as one unit until we have breached through the Alliance defenses around the station.
Then we'll split up and search for Ente. When he is found, send a signal to all others, and we will all try to pull out as quick as
possible."

[Rebel] "This is a high-risk mission of increadible importance. I doubt that all of us will come back. But I'm sure that some of us
will, and will continue doing what they can for the people."

[Rebel] "I have no more to say. Good luck friends."

\subsection{To Peye, interaction}

[Ai] ... "You are actually going to try extracting Ente? That's a suicide mission! Even if some of you managed to slip through
the defenses, you would never be able to escape. By then, we would have pinpointed your locations. We have several
Hangar ships around the research station. You would be dead fishes."

[Ai] "But an interesting thought occured to me. The scientists knows something that they won't share with us.
Maybe Ente is willing to share with the rebels. Then they might lead us there. I will be back in a moment."

...

[Ai] "I have spoken to the command, and I have got green light to go ahead with the plan. I will try to distract the defenses
around the station. It will still be challenging to get through. But not suicidal. Good luck."

\subsection{To Peye, battle}

[Rebel] It seems like we have reached their defenses. The goal is to slip through. Don't do anything risky.

... Level ...

[Rebel] Seems like most of us got through. We are tougher than they think! Now, let's search the station.
When you have found Ente, send the signal. When you receive the signal, pull out as quick as possible."

\subsection{At Peye Outpost - Ente}

[Sair] Let's see. Let's explore that smaller building outside the complex.

... Ship landed ...

You quickly walk into the small hut, looking around, searching for the man in the picture you saw.
Suddenly he appears in one of the door openings. He looks surprised, and a bit nervous. You ask him if
he is Ente.

The man speaks. "Well, yes, I am. I must say I am a bit surprised by your visit. Can you tell me, who might you be? No,
don't tell me. Let me guess."

"Are you another Alliance coming here to persuade me of sharing my information? You look too inexperienced for that.
Maybe you are something else. A rebel? It seems unlikely that a rebel would manage his way here without particular help.."

...

"You are here to bring me to the Rebel Station you say? But your eyes tells me something else. You don't really know
why you are here. You are confused. What is going on, really?"

"I will tell you a little bit more. Maybe we can even help each other a bit here."

"As you know, I am a scientists. As you also probably know, I am part of a small group that have been researching the Murt
for quite some time. The mineral has gotten a lot of attention from Alliance and rebels lately, and rightly so. I wouldn't be
surprised if that mineral will be the single factor that determines the future of this sector."

"Up until now only small amounts has been found at a time around the system. This has been very useful for research, and
has also been crucial for us rigging the beacon network over the system. But the access has been and still is very limited."

"Up until recently, that is. Our scans have shown us a meteorite containing massive amounts of Murt. Thousands of times
more than what we have found up until now combined. It is an unimaginable source of power."

"In the right hands, it could be use to raise the entire sector from poverty, and maybe in the extension even give us the
chance to move on from this sector."

"In the wrong hands... It could be used for such incredible amounts of destruction."

"If the Alliance got their hands on it, they would certainly be able to eliminate the rebels. They would also be able to assert
an iron grip over the entire sector. They have started liking the thought of being the leaders and protectors of the sectors.
With this power, they would be unchallengable."

"On the other hand, if the rebels got their hands on Murt, they would certainly use it to work even harder against the Alliance.
I believe that it initially would be an even struggle, as they don't have the technology to utilize the source properly.
It would lead to a long war. They would probably win in the end, and cause so much suffering on the way."

"I don't think that the sector is ready for this amount of Murt. I hope that it will be one day."

"So what is my suggestion? We can't give it to the Alliance, we can't give it to the rebels, and we cannot destroy it as it would
destroy the only hope for the future that we still have here. The only path I can see is to hide it. Hide it until the sector is ready
to handle it. Hide it from Alliance and rebels alike. When the sector stabilizes one day, in ten or hundred years, we can
bring it out in the open."

Ente eyes you curiously.

"You know. I am telling you all this for a reason. I am hoping for your cooperation. All this information will leak to the Alliance
and the rebels eventually. What I would like you to do before then is to using a particular technology hide the meteor from
all scans."

"To do this, you will need to access one of our information centrals. There you will find information about where to find the
technology, as well as where the meteor is located. There is also gathered information about what has been going on
in the sector the latest years. If I can't convince you, maybe that information can. The Alliance and the rebels both are trying
to keep a good face outwards, but too many of the rumours you have heard are true."

"So, you bring me to the Rebel Base as planned. Then, when an opportunity arises, you'll go to the information hub I will mark 
on your map. When you have the knowledge, you can decide if you believe me, or if you want to provide the information to
the rebels or the Alliance. I will not leak crucial information until I know that you have finished your mission,
and by then it is too late for them to do anything about it."

"Let's go"

[Sair] "What a strange man. But I think that the most logical path for us to at least initially follow his plan. We can always
diverge later and share the information with Ai or Rok later on."

[Sair] "I'll send the signal to the other rebels. Let's move out now."

\subsection{To Rebel Station, battle}

[Sair] "Seems Ai wasn't as successful in diverging the Alliance attention as she hoped to be. This looks like it will be a tough one."

[Rebel] "... We have no choice but trying to break through. Good luck, everyone."

... Breaking out level, with hangar ship ...

[Rebel] "We are through! Let's meet at the Rebel Station!"

\subsection{Outside the Rebel Station}

[Ente] "It seems to be time. Remember what I have told you. Go to the coordinate I marked on your map.
You will find more information there. Make sure that you aren't followed."

"I don't know if we will meet again. I hope you do what's best for the sector."

"Remember. In their own minds all people are their own heroes, defender if their own beliefs.
There are no good people, and there are no bad people. There are just people."

\subsection{Rebel Station}

Rok speaks to the group. "Incredible work, all of you."
He turns to Ente who looks visibly uncomfortable. 

"Welcome to the Rebel Base Ente. We will soon have a little chat you and me."
There is something very unsettling in is voice. He turns to the group of rebel pilots again.

"I will keep in touch. Come back soon, there will definitely be more to do in the near future."

He and Ente leaves the room. While Ente passes he quickly whispers. "Good luck".

\subsection{Outside Rebel Station}

[Sair] "I guess it wouldn't hurt to explore that information hub he was speaking about. And if what he said about the
Murt meteorite is true.. Hiding it might be the correct option."

\end{document}




























