\documentclass[a4paper,12pt]{article}
\usepackage[utf8]
{inputenc}

\begin{document}

\title{Mission 6: In The Name Of Science - v2}
\author{LinkPactGames}
\date{October 2014}
\maketitle

\section{Summary}

\textit{The player is sent on a mission to retrieve a scientist from Peye.
The player has a serious discussion with the scientist, before returning him
to the rebels.}

\section{Story points}

o Rebel Station, Rok: Findings, need to retrieve scentist at Peye\\
o Outside Rebel Station, Sair, rebel: Comments\\
\textgreater To Peye outpost, Ai and Sair: Discussing the situation\\
\textgreater x To Peye outpost, slippin' through Alliance outpost: Breaking through\\
o Outpost, Scientist Ente: Speaking with Ente, introducing possible Murt-plan, and Murt
gathering\\
\textgreater x To Rebel Base: Attacked fiercely by Alliance\\
o Outside Rebel Station, Ente - Comment\\
o Rebel Station, Rok\\
o Outside Rebel Station, Sair - Comment

\section{Manus}

\subsection{Rebel Station}

Rok greets you. He looks worried. 

[Rok] "Welcome back. It is good that you came so quickly."

[Rok] "We didn't find much Murt in the cargo. It seems like they took it of in the last minute.."

[Rok] "On the other hand, we found some interesting conversations in their log system."

[Rok] "They spoke about a group of scientists living near Peye, who have been scanning the solar system for Murt."

[Rok] "They have no particular allegience, neither to the Alliance or us rebels, but have lately been depending on a small
Alliance fleet for their protection."

[Rok] "According to the logged conversation it seems like that the group has found a huge quantity of Murt."

[Rok] "They seem hestitant sharing this information with the Alliance though. They seem worried that the Alliance
would use the Murt for military purposes."

[Rok] "Naturally, the Alliance is very upset about this, and is currently pressuring the scientists to share their information. It is
probably only a matter of time before they get what they want."

[Rok] "That's why we have to act now, as quick as possible."

[Rok] "We have a name to one scientist that seems to be of high importance - Ente." 

[Rok] "He has been deeply involved in the Murt research, and is said to be very sceptical of their relationship to the Alliance. "

[Rok] "We want to bring him here, and to have a.. chat with him." 

[Rok] "We will send a small group of ships to slip through the Alliance's defenses around the research station, 
extract Ente, and return him here."

[Rok] "The idea is simple, but this will likely be a highly dangerous mission." 

[Rok] "You should prepare yourself properly. The rest of the fleet will be waiting close to the rebel base."

\subsection{Outside Rebel Station}

[Sair] "'Bring him here to have a chat with him', that sounds really sinister to me.." 

[Sair] "We shouldn't let our guards down. Remember why we are here." 

[Sair] "We should speak to Ai. Let's do it when we aren't so close to the other ships."

...

[Rebel] "All here? Good." 

[Rebel] "We'll move as one unit until we have passed the Alliance defenses around the station."

[Rebel] "Then we'll split up and search for that scientist." 

[Rebel] "When he is found, send a signal to all others, and we will all try to pull out as quick as possible."

[Rebel] "This is a high-risk mission. I doubt that all of us will come back."

[Rebel] "But I'm sure that some of us will, and that they will continue to do what they can for the people."

[Rebel] "I have no more words for you. Good luck friends."

\subsection{To Peye, interaction}

[Ai] ... "You are seriously going to try to extract Ente?" 

[Ai] "That's a suicide mission.. Even if some of you managed to slip through
the defenses, you would never be able to escape." 

[Ai] "We have several Hangar ships stationed around the research station. You would be dead fishes."

[Ai] "But an interesting thought occured to me." 

[Ai] "The scientists knows something that they won't share with us. Maybe Ente is willing to share with the rebels."

[Ai] "Then the rebels could lead us there.."

[Ai] "I need to speak to the command. I will be back in a moment."

...

[Sair] "It sounds like a utterly mad idea, to let the rebel get the information about Murt, and then shadow them to
the location."

[Sair] "But it isn't impossible that it actually will work.."

...

[Ai] "I have spoken to the command. I have got green light to go ahead with the plan."

[Ai] "I will try to distract the defenses around the station."

[Ai] "It will still be challenging to get through. But not suicidal. You will make it. Good luck."

\subsection{To Peye, battle}

[Rebel] "It seems like we have reached their defenses. The goal is to slip through. Don't do anything risky."

... Level ...

[Rebel] "Seems like most of us got through. We are tougher than they think!" 

[Rebel] "Now, let's search the station."

[Rebel] "If you find Ente, send the signal. If you receive the signal, pull out as quick as possible."

\subsection{At Peye Outpost - Ente}

[Sair] "Let's see. Let's explore that smaller building outside the complex."

... Ship landed ...

You quickly walk into the small hut, looking around, searching for the man in the picture you saw.

A man appears in one of the door openings. He looks surprised, and a bit nervous. You ask him if he is Ente.

[Ente] "Well, yes, I am." 

[Ente] "I must say I am a bit surprised by your visit. Can you tell me, who might you be? 

[Ente] "No, don't tell me. Let me guess."

[Ente] "..."

[Ente] "Are you yet another Alliance coming here to persuade me of sharing my information? 

[Ente] "You look too inexperienced for that. Maybe you are something else." 

[Ente] "A rebel? Probably a rebel. But somehow something about you feels... different."

...

[Ente] "You are here to bring me to the Rebel Station you say?"

[Ente] "But your eyes tells me something else." 

[Ente] "You don't really know why you are here. You are confused. You wonder what's really going on."

[Ente] "I will assume my observations are correct. I will tell you a little bit more. 
Maybe we can even help each other a bit here."

[Ente] "As you know, I am a scientist." 

[Ente] "As you also probably know, I am part of a group that are researching Murt."

[Ente] "We are developing and testing scanners for finding Murt."

[Ente] "Up until now only small amounts has been found at a time around the system." 

[Ente] "This has been very useful for research, but we have only found very small amounts."

[Ente] "Up until recently, that is." 

[Ente] "Our scans have shown us a meteorite containing massive amounts of Murt. 

[Ente] "Thousands of times more than what we have found up until now combined. It is an unimaginable source of power."

[Ente] "In the right hands, it could be an immense help for the people of the sector."

[Ente] "In the wrong hands... It could be used for such incredible amounts of destruction."

[Ente] "..."

[Ente] "You realize the problem here, don't you?"

[Ente] "Currently the whole sector is in conflict. Rebels and Alliance struggle for the control."

[Ente] "The Alliance want to assert full control in order to achieve a calm and controlled sector."

[Ente] "The rebels on the other hand resent this. They want freedom, to let each planet walk its own path, and
are willing to sacrifice the order of the sector for that freedom."

[Ente] "Which way is better? I have no preferences. What I know is that the Murt currently will be used as a tool of war."

[Ente] "We must put the Murt to use, but we must put it to good use. There are no other alternatives."

[Ente] "So what is my suggestion? We must hide the Murt." 

[Ente] "Hide it." 

[Ente] "Hide it until the sector is ready to handle it."

[Ente] "When the sector stabilizes one day, in ten or hundred years, we can bring it out in the open."

Ente eyes you curiously.

[Ente] "You know. I am telling you all this for a reason." 

[Ente] "I want your cooperation." 

[Ente] "All of this information will leak to the Alliance and the rebels eventually." 

[Ente] "We must hide it away before that happens."

[Ente] "To do this, you will need to access one of our information centrals." 

[Ente] "There you will find information about where to find the technology, as well as the exact location of the meteor."

[Ente] "You should bring me to the Rebel Base as planned. Then you should go to the information hub."

[Ente] "I will not leak crucial information until I know that you have finished your mission."

[Ente] "By then it will be too late for them to do anything about it."

[Ente] "Let's go"

The strange man hurries before you up into the ship.

...

[Sair] "What a strange man. It seems the most logical path for us to at least initially follow his plan."

[Sair] "We can always diverge later and share the information with Ai or Rok later on."

[Sair] "I'll send the signal to the other rebels. Let's move out now."

\subsection{To Rebel Station, battle}

[Sair] "Seems Ai wasn't as successful in diverging the Alliance attention as she hoped to be. This looks like it will be a tough one."

[Rebel] "... We have no choice but trying to break through. Good luck, everyone."

... Breaking out level, with hangar ship ...

[Rebel] "We are through! Let's meet at the Rebel Station!"

\subsection{Outside the Rebel Station}

[Ente] "It seems to be time. Remember what I have told you." 

[Ente] "Go to the coordinate I marked on your map. You will find more information there."

[Ente] "Make sure that you aren't followed."

[Ente] "I don't know if we will meet again. I trust that you will do what's best for the sector."

[Ente] "Remember. In their own minds all people are their own heroes, defender if their own beliefs."

[Ente] "There are no good people, and there are no bad people. There are just people."

\subsection{Rebel Station}

Rok speaks to the group. 

[Rok] "Incredible work, all of you."

He turns to Ente who looks visibly uncomfortable. Rok bears a slightly sinister look.

[Rok] "Welcome to the Rebel Base Ente. We will soon have a little chat you and me."

There is something very unsettling in is voice. He turns to the group of rebel pilots again.

"I will keep in touch. Come back soon, there will definitely be more to do in the near future."

He and Ente leaves the room. While Ente passes he quickly whispers to you. 

[Ente] "Good luck"

\subsection{Outside Rebel Station}

[Sair] "We should go to that information hub he was speaking about."

[Sair] "And if what he said about the Murt meteorite is true.. Hiding it might be the correct option."

[Sair] "Let's not contact Ai just yet.."

\end{document}




























