\documentclass[a4paper,12pt]{article}
\usepackage[utf8]
{inputenc}

\begin{document}

\title{Mission 10: The End, Rebel branch - v1}
\author{LinkPactGames}
\date{October 2014}
\maketitle

\section{Summary}

\textit{The player helps the rebels accessing and keeping control over Murt. The tides are turned.
The sector now has two dominant factions, and is thrown into a deeper war.}

\section{Story points}

o Rebel fleet, Rok - Rok explains rebel position
\textgreater Asteroid belt - The player and the rebels move in, seizing the Murt.
ox Murt - The rebels defends Murt, extracting, and beating back the Alliance
\textgreater \textgreater Rebel Ending

\section{Manus}

\subsection{Rebel Fleet}

[Rok] "There you are! I'm glad you are here."

[Rok] "I don't know how much you know about the situation. As said, the scientist leaked after some persuading.
He told us about this enourmous quantities of Murt, which apparently is located somewhere in this asteroid belt."

[Rok] "It is only a matter of time before our sensors will pick up which asteroid that contains the Murt. When we do,
we will hurry there and take control over it as quick as possible."

[Rok] "We were here before the Alliance, and we will probably get to the Murt before them. They have a stronger force
here through, so it is crucial that we will be able to hold them of for long enough.."

[Rok] "Your help is really appreciated here. We could move out any minute now, so stay here and stay alert."

Do you want to share what you now about Murt with Rok?
> Tell him what you know
> Not yet, I want to check the other options

[Rok] "So that was what you were doing? And the scout fleet, what that you?"

[Rok] "We don't have time for scolding now anyway. If this is true, this information could tip this entire situation in our favour.
We are moving out immediately."

\subsection{Asteroid Belt}

[Rok] "An Alliance scout team! We must shatter them. We can't lead them to the Murt."

... Level against light Alliance ships ...

\subsection{Murt}

[Rok] "Yes! It must be that asteroid. It looks perfectly ordinary, but our sensors beg to differ. Let's start the extraction."

[Rok] "We have a team that has started the drilling. We have prepared energy cells that are able to handle the Murt.
When they are ready, we will be able to assert control here. Well done, well done!"

[Rok] "There is a large Alliance force incoming. We must hold them of for long enough."

[Rok] "This will be the final battle. We can't lose now. Keep it tight everyone."

... Survive a certain time level ...

[Rok] "We have access to the Murt! Quickly, equip those energy cells to your ships. With those, both the shields and the
weapons will overflow with power. We will be invincible and immensely powerful."

[Rok] "We can finally pay back for all they have done to us! We can finally get revenge for all of our people they have killed!"

[Rok] "We can finally eradicate the Alliance!" 

... Final overpowered level ... [Featuring desperate messages from the Alliance]

... Fades out into the outro

\subsection{Ending}

[TO BE WRITTEN]

\end{document}




























